### 2017-07-11 Papers/DroneInTheWind.tex
First Report Tex File

% Specify the type of document
\documentclass[12pt]{article}

% Load a number of useful packages
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
 \usepackage[margin=1.0in]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{float}

% Two more packages that make it easy to show MATLAB code
\usepackage[T1]{fontenc}
\usepackage[framed,numbered]{matlab-prettifier}
\lstset{
	style = Matlab-editor,
	basicstyle=\mlttfamily\small,
}

% Say where pictures (if any) will be placed
\graphicspath{{./pictures/}}

% Define title, author, and date
\title{Drones in Wind}
\author{Nico Alba, Isabel Anderson, Emilio Gordon, Michael Gray}
\date{July, 2017}

% Start of document
\begin{document}

% Put the title, author, and date at top of first page
\maketitle

\section{Goal}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                 Model                                                                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                              Controller                                                                               %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Controller and Optimization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                               Controller                                                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Controller}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                               OptimTraj                                                                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{OptimTraj}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Analysis                                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}
% Display list of references in IEEE Transactions format.
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}

% End of document (everything after this is ignored)
\end{document}

### 2017-07-13 Papers/DroneInTheWind.tex
Goal Section of the report written.

@@
 \section{Goal}
+The "Drones in Wind" simulation simulates the flight of a quadcopter drone.
+The drone in the simulation will be modeled after the AscTec Pelican, a research-drone by the German company Ascending Technologies.
+The simulated drone as of the point of writing this paper is equipped with sensors to measure the velocity in the horizontal and vertical axis, the vertical position and the pitch angle.
+\newline \newline
+The goal is to create a controller that linearizes about a trajectory given by the third-party program OptimTraj.
+The trajectory comes from a cost function that minimizes time.
+A requirement for this model is established such that the time of multiple completed simulations will have a coefficient of variation less than one.
+Since the simulation should be of an optimized trajectory, minimal variations should be expected.
+With this requirement in mind, a procedure for verification is established.
+Verification ensures that the system meets the established requirements.
+Verification will be conducted through several methodologies and are as follows
+\begin{itemize}
+\item Data will be acquired for up to 100 flight simulations. This will be done by implementing the script shown in Figure \ref{fig:fgc}.
+\item Using Matlab, a histogram can be created in order to visualize the frequency of the drones flight times. 
+\item Using Matlab, the coefficient of variation will be calculated can be computed for the acquired data.
+\begin{figure}[H]
+\begin{quote}
+\begin{lstlisting}
+% Number of flights
+nFlights = 100;
+% Loop over each flight
+for i=1:nFlights
+    % Run simulation without graphics and save data
+    DesignProblem0('Controller','datafile','data.mat','display',false);
+    % Load data
+    load('data.mat');
+    % Get t and x
+    t = processdata.t
+    x = processdata.x
+    % DOUBLE CHECK THE CODE.
+end
+\end{lstlisting}
+\end{quote}
+\caption{Flight Generation Code\label{fig:fgc}}
+\end{figure}
+\end{itemize}
 
@@
 \section{Analysis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                                Future Work                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Future Work}
 % Display list of references in IEEE Transactions format.

### 2017-07-13 Controller.m
Controller was corrupted during sync
Controller was corrupted during first sync can stored all of githubs
comments i.e. >>>>>>> origin/master.
Removed these and got it working.

@@ -30,26 +30,6 @@ func.init = @initControlSystem;
 func.run = @runControlSystem;
 end
 
-<<<<<<< HEAD
-%
-% STEP #1: Modify, but do NOT rename, this function. It is called once,
-% before the simulation loop starts.
-%
-
-function [actuators,data] = initControlSystem(sensors,references,parameters,data)
-[actuators,data] = runControlSystem(sensors,references,parameters,data);
-end
-
-%
-% STEP #2: Modify, but do NOT rename, this function. It is called every
-% time through the simulation loop.
-%
-
-function [actuators,data] = runControlSystem(sensors,references,parameters,data)
-actuators.thrust = 0;
-actuators.pitchrate = 0;
-end
-=======
 
 function [actuators,data] = initControlSystem(sensors,references,parameters,data)
 
@@ -117,5 +97,8 @@ state = [sensors.x; sensors.xdot; sensors.z; sensors.zdot; sensors.theta] - ...
 input = -K*state;
 actuators.thrust = input(2) + parameters.g;
 actuators.pitchrate = input(1);
+
+if (sensors.xdot==0 && sensors.zdot == 0)
+    data.timeEnd = t
 end
->>>>>>> origin/master
+end

### 2017-07-13 multipleFlights.m

@@ -1,0 +1,36 @@
+% Number of flights
+nFlights = 100;
+
+%Vars
+Xf = zeros(1,nFlights);
+xx = []
+tt = []
+% Loop over each flight
+tic
+for i=1:nFlights
+% Run simulation without graphics and save data
+DesignProblemSummer2017('Controller')% Load data
+load('data.mat');
+% Get t and x
+t = processdata.timeEnd;
+tt = [tt t];
+ii = [ii i];
+% Do analysis...
+%
+Xf(i) = x(end);
+end
+toc
+histogram(Xf)
+    set(gca,'fontsize',14);
+    xlabel('Distance (x)');
+    ylabel('Frequency');
+    set(gcf,'paperorientation','landscape');
+    set(gcf,'paperunits','normalized');
+    set(gcf,'paperposition',[0 0 1 1]);
+    title('Frequency Distribution of 1000 Simulated Flights')
+    print(gcf,'-dpdf','flights.pdf');
+mean(Xf)
+median(Xf)
+
+m = matfile(xFlight1,'Writable',isWritable)
+save(xFlight,Xf)

### 2017-07-15 DesignProblemSummer2017.m
changed speedracer back to controller

@@ -279,7 +279,7 @@ if (isempty(fig))
         color = 'r';
     end
     fig.text.status=text(0.05,0.975,...
-        sprintf('SPEED RACER: %s',status),... % MODIFICATION
+        sprintf('CONTROLLER: %s',status),... % MODIFICATION
         'fontweight','bold','fontsize',fs,...
         'color',color,'verticalalignment','top');
     fig.text.time=text(0.05,0.12,...
@@ -331,7 +331,7 @@ else
         status = 'OFF';
         color = 'r';
     end
-    set(fig.text.status,'string',sprintf('SPEED RACER: %s',status),'color',color);%Modification
+    set(fig.text.status,'string',sprintf('CONTROLLER: %s',status),'color',color);%Modification
     
     % Quadcopter
     fig.view0.spar = DrawBox(fig.view0.spar,...

### 2017-07-15 Controller.m
fixed output of final time, made analysis graph more clear

@@ -61,6 +61,11 @@ data.trajZdot = x(4,:);
 data.trajTheta = x(5,:);
 data.trajIND = 1;
 
+% Analysis variables
+data.stationaryVelocityMargin = .01; % Required velocity from rest (for both x and z)
+data.finalPositionMargin = .01; % Required distance from final position (for both x and z)
+data.endBool = 0; % Used to only display the end time once
+
 % Run the controller
 [actuators,data] = runControlSystem(sensors,references,parameters,data);
 end
@@ -98,7 +103,13 @@ input = -K*state;
 actuators.thrust = input(2) + parameters.g;
 actuators.pitchrate = input(1);
 
-if (sensors.xdot==0 && sensors.zdot == 0)
-    data.timeEnd = t
+if abs(sensors.xdot) < data.stationaryVelocityMargin && ...
+        abs(sensors.zdot) < data.stationaryVelocityMargin && ...
+        abs(sensors.x - data.trajX(end)) < data.finalPositionMargin && ...
+        abs(sensors.z - data.trajZ(end)) < data.finalPositionMargin && ...
+        data.endBool == 0
+    data.endBool = 1;
+    data.timeEnd = data.trajT(ind);
+    fprintf('End State Achieved at: %f seconds\n', data.timeEnd)
 end
 end

### 2017-07-15 DesignProblemSummer2017.m

@@ -80,7 +80,7 @@ function [process,controller] = SetupSimulation(process)
 % - State time.
 process.tStart = 0;
 % - Stop time.
-process.tStop = 5;
+process.tStop = 5; % MODIFICATION: Runtime
 % - Time step.
 process.tStep = 1/50;
 % - Names of things to log in datafile, if desired
@@ -232,7 +232,7 @@ w = U(1,1);
 f = U(2,1);
 % compute rates of change
 d_x = xdot;
-d_xdot = (f/process.m)*sin(theta)+0; %MODIFICATION: Wind
+d_xdot = (f/process.m)*sin(theta) + 0; %MODIFICATION: Wind
 d_z = zdot;
 d_zdot = (f/process.m)*cos(theta)-process.g;
 d_theta = w;
@@ -279,7 +279,7 @@ if (isempty(fig))
         color = 'r';
     end
     fig.text.status=text(0.05,0.975,...
-        sprintf('CONTROLLER: %s',status),... % MODIFICATION
+        sprintf('CONTROLLER: %s',status),...
         'fontweight','bold','fontsize',fs,...
         'color',color,'verticalalignment','top');
     fig.text.time=text(0.05,0.12,...
@@ -331,7 +331,7 @@ else
         status = 'OFF';
         color = 'r';
     end
-    set(fig.text.status,'string',sprintf('CONTROLLER: %s',status),'color',color);%Modification
+    set(fig.text.status,'string',sprintf('CONTROLLER: %s',status),'color',color);
     
     % Quadcopter
     fig.view0.spar = DrawBox(fig.view0.spar,...

### 2017-07-15 analysis.m

@@ -10,8 +10,8 @@ w = controllerdata.actuators.pitchrate;
 %plot(t,x,t,xdot,t,z,t,zdot,t,theta)
 plot(t,f)
 %legend('x','xdot','z','zdot','theta')
-xlabel('time')
+xlabel('Time, t')
 %ylabel('m, m/s, rad')
-ylabel('N')
-title('3 Second, input minimizing')
+ylabel('Thrust, N')
+title('5 Second, error minimizing')
 grid on

### 2017-07-15 planOptimalTrajectory.m

@@ -3,7 +3,7 @@ addpath OptimTraj/
 
 maxThrust = 15;
 maxPitchRate = 5;
-duration = 2;
+duration = 5;
 xInitial = 0;
 zInitial = 0;
 xFinal = 1;

### 2017-07-20 Papers/DroneInTheWind.tex
Clarified cost function in intro
Added messy linearization section, needs to be made to look nicer, note that the PDF file has not changed and therefore does not reflect the current .tex file

@@
 The goal is to create a controller that linearizes about a trajectory given by the third-party program OptimTraj.
-The trajectory comes from a cost function that minimizes time.
+The trajectory comes from a cost function that minimizes the time integral of error from a desired position.
 A requirement for this model is established such that the time of multiple completed simulations will have a coefficient of variation less than one.
@@
 \section{Model}
+
+The state for the system is defined as
+\begin{equation}
+\label{state}
+x = \begin{bmatrix} x\\ \dot{x} \\ z \\ \dot{z} \\ \theta \end{bmatrix}
+\end{equation}
+
+Where $x$, $z$, correspond to horizontal and vertical position, respectively, and $\theta$ corresponds to the angle of the quad from upright.
+
+The inputs for the system are defined as
+
+\begin{equation}
+\label{inputs}
+u = \begin{bmatrix} \omega \\ f \end{bmatrix}
+\end{equation}
+
+Where $\omega$ corresponds to angular pitch rate and $f$ corresponds to thrust.
+Taking the jacobian lends the following A and B matrices
+
+\begin{equation}
+\label{A_matrix}
+A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && \frac{f\cos{\theta}}{m} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && \frac{-f\sin{\theta}}{m} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+\label{B_matrix}
+B = \begin{bmatrix} 0 && 0 \\ 0 && \frac{\sin{\theta}}{m} \\ 0 && 0 \\ 0 && \frac{\cos{\theta}}{m} \\ 1 && 0 \end{bmatrix}
+\end{equation}
+
+We have no need to substitute in equilibrium conditions because we are linearizing about a trajectory.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-07-24 Papers/DroneInTheWind.tex
Revised linearization section in .tex Added controller section in .tex Changed the equilibrium addition in the thrust input from g to m*g (mass is currently 1 so this will change nothing, but in the future mass might change)

@@
 \begin{equation}
+\label{A_matrix_intermediate}
+A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && \frac{f\cos{\theta}}{m} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && \frac{-f\sin{\theta}}{m} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+\label{B_matrix_intermediate}
+B = \begin{bmatrix} 0 && 0 \\ 0 && \frac{\sin{\theta}}{m} \\ 0 && 0 \\ 0 && \frac{\cos{\theta}}{m} \\ 1 && 0 \end{bmatrix}
+\end{equation}
+
+We now substitute in the equilibrium force, $f = mg$, lending the following matrices
+
+\begin{equation}
 \label{A_matrix}
-A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && \frac{f\cos{\theta}}{m} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && \frac{-f\sin{\theta}}{m} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
+A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && g\cos{\theta} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && -g\sin{\theta} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
 \end{equation}
@@
 
-We have no need to substitute in equilibrium conditions because we are linearizing about a trajectory.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Controller}
+The controller is designed to use in the loop control with LQR to follow a given trajectory.
+
+First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ is the only variable.
+These symbolic descriptions are then turned into MATLAB functions and saved in the data struct.
+The Q and R weight matrices are then initialized.
+The init function proceeds to load in the trajectory data and also adds it to the data struct.
+Finally, some parameters used to determine when the quad has reached its destination are initialized.
+
+Logic is used at the start of the control loop to determine if there is still trajectory data available for the current timestep.
+If there is not, the controller will linearize about the last available trajectory point.
+This case does not happen in current simulations because the trajectory is planned for the entire duration of the simulation.
+
+After determining that the simulation is still within the regime in which a trajectory is available, the controller will find the respective trajectory point to linearize about for the current timestep.
+The angle for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
+
+Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being pitch rate and the second being thrust.
+Note here that the thrust is augmented by the equilibrium condition for hover, $f = mg$.
+$K$ is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-07-24 Controller.m

@@ -100,8 +100,8 @@ K = lqr(A,B,data.Q,data.R);
 state = [sensors.x; sensors.xdot; sensors.z; sensors.zdot; sensors.theta] - ...
     [trajX; trajXdot; trajZ; trajZdot; trajTheta];
 input = -K*state;
-actuators.thrust = input(2) + parameters.g;
 actuators.pitchrate = input(1);
+actuators.thrust = input(2) + parameters.g*parameters.m;
 
 if abs(sensors.xdot) < data.stationaryVelocityMargin && ...
         abs(sensors.zdot) < data.stationaryVelocityMargin && ...

### 2017-07-24 Papers/DroneInTheWind.tex
minor formatting changes

@@
 
-Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being pitch rate and the second being thrust.
+Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.
 Note here that the thrust is augmented by the equilibrium condition for hover, $f = mg$.
-$K$ is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.
+K is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.
 

### 2017-07-25 Papers/DroneInTheWind.tex
Report Changes
Cleaned the intro section and removed the goal and verifications.
Clarified points in Model Section.

ToDo:
Insert models/equations/matrices into Controller section.
Add Analysis and Future Work.

@@
 The simulated drone as of the point of writing this paper is equipped with sensors to measure the velocity in the horizontal and vertical axis, the vertical position and the pitch angle.
-\newline \newline
 The goal is to create a controller that linearizes about a trajectory given by the third-party program OptimTraj.
 The trajectory comes from a cost function that minimizes the time integral of error from a desired position.
-A requirement for this model is established such that the time of multiple completed simulations will have a coefficient of variation less than one.
-Since the simulation should be of an optimized trajectory, minimal variations should be expected.
-With this requirement in mind, a procedure for verification is established.
-Verification ensures that the system meets the established requirements.
-Verification will be conducted through several methodologies and are as follows
-\begin{itemize}
-\item Data will be acquired for up to 100 flight simulations. This will be done by implementing the script shown in Figure \ref{fig:fgc}.
-\item Using Matlab, a histogram can be created in order to visualize the frequency of the drones flight times. 
-\item Using Matlab, the coefficient of variation will be calculated can be computed for the acquired data.
-\begin{figure}[H]
-\begin{quote}
-\begin{lstlisting}
-% Number of flights
-nFlights = 100;
-% Loop over each flight
-for i=1:nFlights
-    % Run simulation without graphics and save data
-    DesignProblem0('Controller','datafile','data.mat','display',false);
-    % Load data
-    load('data.mat');
-    % Get t and x
-    t = processdata.t
-    x = processdata.x
-    % DOUBLE CHECK THE CODE.
-end
-\end{lstlisting}
-\end{quote}
-\caption{Flight Generation Code\label{fig:fgc}}
-\end{figure}
-\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Model}
-
-The state for the system is defined as
-\begin{equation}
+The motion of the drone is governed by the ordinary differential equations with the state defined as
+\begin{equation*}
 \label{state}
 x = \begin{bmatrix} x\\ \dot{x} \\ z \\ \dot{z} \\ \theta \end{bmatrix}
-\end{equation}
-
-Where $x$, $z$, correspond to horizontal and vertical position, respectively, and $\theta$ corresponds to the angle of the quad from upright.
-
-The inputs for the system are defined as
-
-\begin{equation}
+\end{equation*}
+such that $x$, $z$, correspond to horizontal and vertical position, respectively, and $\theta$ corresponds to the angle of the quad from upright. The inputs for the system are defined as
+\begin{equation*}
 \label{inputs}
 u = \begin{bmatrix} \omega \\ f \end{bmatrix}
-\end{equation}
-
-Where $\omega$ corresponds to angular pitch rate and $f$ corresponds to thrust.
-Taking the jacobian lends the following A and B matrices
-
+\end{equation*}
+such that $\omega$ corresponds to angular pitch rate and $f$ corresponds to thrust.
+Taking the jacobian lends the following A and B matrices shown by Equation \ref{A_matrix_intermediate} and Equation \ref{B_matrix_intermediate}
 \begin{equation}
@@
 \end{equation}
-
-We now substitute in the equilibrium force, $f = mg$, lending the following matrices
-
+Substituting the equilibrium force, $f = mg$, results in the following matrices shown in Equation \ref{A_matrix} and Equation \ref{B_matrix}.
 \begin{equation}
@@
 The controller is designed to use in the loop control with LQR to follow a given trajectory.
-
 First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ is the only variable.
@@
 Finally, some parameters used to determine when the quad has reached its destination are initialized.
-
+\newline
+\newline
 Logic is used at the start of the control loop to determine if there is still trajectory data available for the current timestep.
@@
 This case does not happen in current simulations because the trajectory is planned for the entire duration of the simulation.
-
+\newline
+\newline
 After determining that the simulation is still within the regime in which a trajectory is available, the controller will find the respective trajectory point to linearize about for the current timestep.
 The angle for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
-
+\newline
+\newline
 Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.

### 2017-07-25 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex

@@
 \usepackage{float}
-
+\usepackage{float}
+\usepackage{enumitem}
+\setlist{nosep,after=\vspace{\baselineskip}}
 % Two more packages that make it easy to show MATLAB code
@@
 The motion of the drone is governed by the ordinary differential equations with the state defined as
-\begin{equation*}
+\begin{equation}
 \label{state}
 x = \begin{bmatrix} x\\ \dot{x} \\ z \\ \dot{z} \\ \theta \end{bmatrix}
-\end{equation*}
+\end{equation}
 such that $x$, $z$, correspond to horizontal and vertical position, respectively, and $\theta$ corresponds to the angle of the quad from upright. The inputs for the system are defined as
-\begin{equation*}
+\begin{equation}
 \label{inputs}
 u = \begin{bmatrix} \omega \\ f \end{bmatrix}
-\end{equation*}
+\end{equation}
 such that $\omega$ corresponds to angular pitch rate and $f$ corresponds to thrust.
-Taking the jacobian lends the following A and B matrices shown by Equation \ref{A_matrix_intermediate} and Equation \ref{B_matrix_intermediate}
+Taking the Jacobian lends the following A and B matrices shown by Equation \ref{A_matrix_intermediate} and Equation \ref{B_matrix_intermediate}
 \begin{equation}
@@
 \subsection{OptimTraj}
+
+OptimTraj \textcolor{red}{(Citation needed)} was used for trajectory planning.
+OptiTraj is a MATLAB library designed by a Cornell PHD student, Matthew P.
+Kelly, to solve for continuous-time single-phase trajectory optimization problems.
+For OptimTraj to solve the optimal trajectory, you must specify various parameters of your problem, including:
+\begin{itemize}
+  \item Dynamics
+  \item Objective function
+  \item Bounds
+  \item Initial trajectory guesses
+\end{itemize}
+
+\begin{flushleft}
+{\Large \textbf{\textbf{Function Dynamics}} }
+\end{flushleft}
+We begin by setting up the function dynamics, \lstinline!problem.func.dynamics!, as explained in the \textbf{Model} section above: 
+\begin{quote}
+\begin{lstlisting}
+syms xdot x zdot z theta w thrust real
+EOMs= [xdot;
+       (thrust/mass)*sin(theta);
+       zdot;
+       (thrust/mass)*cos(theta)-gravity;
+       w];
+
+numf = matlabFunction(EOMs,'vars',[x xdot z zdot theta w thrust]);
+problem.func.dynamics= @(t,x,u) numf( x(1,:),x(2,:),x(3,:),x(4,:),x(5,:),
+                                      u(1,:), u(2,:)) );
+
+\end{lstlisting}
+\end{quote}
+
+\begin{flushleft}
+{\Large \textbf{\textbf{Problem Bounds}} }
+\end{flushleft}
+
+The next step is to set up the \lstinline!problem.func.dynamics!. For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in \textbf{Table 1} below.
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{ |p{2.5cm}||p{2cm}|p{3cm}| }
+ \hline
+ \multicolumn{3}{|c|}{\textbf{Table 1}   Problem Bounds} \\
+ \hline
+ Parameter & Value & Description\\
+ \hline
+ $t_{i}$   & 0 s  & Initial time\\
+ $t_{f}$  & 5 s  & Final time\\
+ $\underline{F}/m$ & 0 m/$s^{2}$ & Min thrust\\
+ $\overline{F}/m$ & 15 m/$s^{2}$ & Max thrust\\
+ $\overline{\omega}$ & 5 rad/s & Max pitch rate \\
+ \hline
+\end{tabular}
+\end{center}
+\end{figure}
+
+\clearpage
+
+\begin{flushleft}
+{\Large \textbf{\textbf{Cost Function}} }
+\end{flushleft}
+You can optimize for a certain aspect using a cost function. The cost functions for different things are shown below. 
+\begin{quote}
+\begin{lstlisting}
+% Input:
+problem.func.pathObj = @(t,x,u)( sum(u.^2,1) );
+
+% Thrust:
+problem.func.pathObj = @(t,x,u)( sum(u(2,:).^2,1) );
+
+% Pitch Rate:
+problem.func.pathObj = @(t,x,u)( sum(u(1,:).^2,1) );
+
+% time
+problem.func.pathObj = @(t,x,u)( sum((x(1,:)-x_f).^2,1) 
+                                +sum((x(3,:)-z_f).^2,1))
+
+\end{lstlisting}
+\end{quote}
+
+\begin{flushleft}
+{\Large \textbf{\textbf{Initialize Guess}} }
+\end{flushleft}
+
+Lastly, before running the solution, the solver must be initialized.
+This is done with the mandatory \lstinline!problem.guess!
+struct.
+Where $x_{i}$ and $x_{f}$ are the desired initial and final states, respectively.
+Additionally, $u_{i}$ and $u_{f}$ are the desired initial and final input, respectively.
+
+\begin{figure}[H]
+\begin{equation*}
+\lstinline!problem.guess.time! = [t_{i}, t_{f}]
+\end{equation*}
+\begin{equation*}
+\lstinline!problem.guess.state! = [x_{i}, x_{f}]
+\end{equation*}
+\begin{equation*}
+\lstinline!problem.guess.control! = [u_{i}, u_{f}] 
+\end{equation*}
+\end{figure}
+\begin{flushleft}
+{\Large \textbf{\textbf{Options}} }
+\end{flushleft}
+
+You can add options using \lstinline!problem.options!, which include amount of details change accuracy settings, and select different solution methods.
+Different methods include trapezoid, Hermite Simpson, Chebyshev, and the Runge Kutta method.
+\newline
+
+\begin{flushleft}
+{\Large \textbf{\textbf{Solution}} }
+\end{flushleft}
+Finally, to solve, the command \lstinline!soln = optimTraj(problem)! is run. You can then unpack the simulation, save the data, and plot out
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-07-26 Papers/DroneInTheWind.tex
Future Work Section Added

@@
 \section{Analysis}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Future Work}
+With the completion of a 2D optimized drone path, plans to enhance the simulation are underway.
+Several additions will be added to the current simulation in order to complete this task.
+Those are as follows
+\newline
+\begin{itemize}
+  \item Implement 3D rigid body dynamics
+  \item Implement additional aerodynamic forces such as drag and ground effect
+\end{itemize}
+With these immediate goals in mind, an accurate simulation can be created to further test the overarching research initiative.
 % Display list of references in IEEE Transactions format.

### 2017-07-26 Papers/DroneInTheWind.tex
Analysis

@@
 \end{equation}
-such that $x$, $z$, correspond to horizontal and vertical position, respectively, and $\theta$ corresponds to the angle of the quad from upright. The inputs for the system are defined as
+such that $x$ and $z$ correspond to horizontal and vertical position, respectively, while $\theta$ corresponds to the angle of the quad from upright. The inputs for the system are defined as
 \begin{equation}
@@
 \section{Analysis}
-
+A method that computes quadcopter trajectories satisfying the minimal principle with respect to time-optimality has been developed.
+The method is based on the two-dimensional quadcopter model with an optimal trajectory created using OptimTraj.
+By defining the dynamics, bounds and cost function the algorithm was able to create an optimal path for which the drone was to follow.
+Testing this method, the simulated drone accomplished moving from a position (0,0) to (1,1) in a time optimal manner.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-07-29 Controller.m
planOptimalTraj.m changed to actual time optimal Controller.m modified to fix bugs with this change

@@ -48,7 +48,7 @@ data.funcA = matlabFunction(A);
 data.funcB = matlabFunction(B);
 
 % Initialize LQR matrices
-data.Q = 2000*eye(5);
+data.Q = 1000*eye(5);
 data.R = eye(2);
 
 % Trajectory
@@ -83,11 +83,12 @@ if (data.trajIND<length(data.trajT))
     trajZdot = data.trajZdot(ind);
     trajTheta = data.trajTheta(ind);
 else
-    trajX = data.trajX(ind);
-    trajXdot = data.trajXdot(ind);
-    trajZ = data.trajZ(ind);
-    trajZdot = data.trajZdot(ind);
-    trajTheta = data.trajTheta(ind);
+    data.trajIND = data.trajIND+1;
+    trajX = data.trajX(end);
+    trajXdot = data.trajXdot(end);
+    trajZ = data.trajZ(end);
+    trajZdot = data.trajZdot(end);
+    trajTheta = data.trajTheta(end);
 end
 
 % Linearize
@@ -109,7 +110,7 @@ if abs(sensors.xdot) < data.stationaryVelocityMargin && ...
         abs(sensors.z - data.trajZ(end)) < data.finalPositionMargin && ...
         data.endBool == 0
     data.endBool = 1;
-    data.timeEnd = data.trajT(ind);
+    data.timeEnd = parameters.tStep*ind;
     fprintf('End State Achieved at: %f seconds\n', data.timeEnd)
 end
 end

### 2017-07-29 analysis.m

@@ -13,5 +13,5 @@ plot(t,f)
 xlabel('Time, t')
 %ylabel('m, m/s, rad')
 ylabel('Thrust, N')
-title('5 Second, error minimizing')
+title('5 Second, time optimal')
 grid on

### 2017-07-29 planOptimalTrajectory.m

@@ -7,7 +7,7 @@ duration = 5;
 xInitial = 0;
 zInitial = 0;
 xFinal = 1;
-zFinal = 1;
+zFinal = 0;
 m = 1;
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
@@ -24,8 +24,9 @@ numf = matlabFunction(f,'vars',[x xdot z zdot theta thrust w]);
 
 problem.func.dynamics = @(t,x,u)( numf(x(1,:), x(2,:), x(3,:), x(4,:), ... 
     x(5,:), u(1,:), u(2,:)) );
-problem.func.pathObj = @(t,x,u)( sum((x(1,:)-xFinal).^2,1) + sum((x(3,:)-zFinal).^2,1) );
+%problem.func.pathObj = @(t,x,u)( sum((x(1,:)-xFinal).^2,1) + sum((x(3,:)-zFinal).^2,1) );
 %problem.func.pathObj = @(t,x,u)( sum(u.^2,1) );
+problem.func.bndObj = @(t0,x0,tF,xF)(tF-t0);
 
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
@@ -34,7 +35,7 @@ problem.func.pathObj = @(t,x,u)( sum((x(1,:)-xFinal).^2,1) + sum((x(3,:)-zFinal)
 
 problem.bounds.initialTime.low = 0;
 problem.bounds.initialTime.upp = 0;
-problem.bounds.finalTime.low = duration;
+problem.bounds.finalTime.low = 0;
 problem.bounds.finalTime.upp = duration;
 
 problem.bounds.initialState.low = [xInitial; 0; zInitial; 0; 0];
@@ -81,7 +82,7 @@ soln = optimTraj(problem);
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 
 %%%% Unpack the simulation
-t = linspace(soln.grid.time(1), soln.grid.time(end), duration*50);
+t = linspace(soln.grid.time(1), soln.grid.time(end), soln.grid.time(end)*50);
 x = soln.interp.state(t);
 u = soln.interp.control(t);
 

### 2017-07-29 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex

@@
 \title{Drones in Wind}
-\author{Nico Alba, Isabel Anderson, Emilio Gordon, Michael Gray}
+\author{Nico Alba, Isabel Anderson, Emilio Gordon, Michael Gray, Will Reyes}
 \date{July, 2017}
@@
 
-OptimTraj \textcolor{red}{(Citation needed)} was used for trajectory planning.
+OptimTraj \cite{OptimTraj} was used for trajectory planning.
 OptiTraj is a MATLAB library designed by a Cornell PHD student, Matthew P.
@@
 
-\begin{flushleft}
-{\Large \textbf{\textbf{Function Dynamics}} }
-\end{flushleft}
-We begin by setting up the function dynamics, \lstinline!problem.func.dynamics!, as explained in the \textbf{Model} section above: 
+\subsubsection{Function Dynamics}
+The simulations begins by setting up the function dynamics, \lstinline!problem.func.dynamics!, as explained in the \textbf{Model} section above: 
 \begin{quote}
@@
 
-\begin{flushleft}
-{\Large \textbf{\textbf{Problem Bounds}} }
-\end{flushleft}
-
+\subsubsection{Problem Bounds}
 The next step is to set up the \lstinline!problem.func.dynamics!. For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in \textbf{Table 1} below. 
-
 \begin{figure}[H]
 \begin{center}
-\begin{tabular}{ |p{2.5cm}||p{2cm}|p{3cm}| }
+\begin{tabular}{ |p{2.5cm}||p{2cm}||p{3cm}| }
  \hline
@@
 
-\begin{flushleft}
-{\Large \textbf{\textbf{Cost Function}} }
-\end{flushleft}
-You can optimize for a certain aspect using a cost function. The cost functions for different things are shown below. 
+\subsubsection{Cost Function}
+Using a cost function, an optimized trajectory around any aspect of the simulation can be found. The cost functions available for different variables are shown below. 
 \begin{quote}
@@
 
-\begin{flushleft}
-{\Large \textbf{\textbf{Initialize Guess}} }
-\end{flushleft}
-
+\subsubsection{Initialize Guess}
 Lastly, before running the solution, the solver must be initialized.
@@
 \end{figure}
-\begin{flushleft}
-{\Large \textbf{\textbf{Options}} }
-\end{flushleft}
-
-You can add options using \lstinline!problem.options!, which include amount of details change accuracy settings, and select different solution methods.
+\subsubsection{Options}
+Additional options are available using \lstinline!problem.options!, which include details to change accuracy settings and select different solution methods.
 Different methods include trapezoid, Hermite Simpson, Chebyshev, and the Runge Kutta method.
-\newline
-
-\begin{flushleft}
-{\Large \textbf{\textbf{Solution}} }
-\end{flushleft}
-Finally, to solve, the command \lstinline!soln = optimTraj(problem)! is run. You can then unpack the simulation, save the data, and plot out
+\subsubsection{Solution}
+Finally, running the command \lstinline!soln = optimTraj(problem)! is used to solve. Following this, it is possible to unpack the simulation, save the data, and plot out.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Display list of references in IEEE Transactions format.
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,references}
+\clearpage
+% Display list of references in IEEE format.
+\begin{thebibliography}{9}
+\bibitem{OptimTraj} 
+MatthewPeterKelly
+\textit{OptimTraj}
+GitHub
+\\\texttt{https://github.com/MatthewPeterKelly/OptimTraj}
+\end{thebibliography}
 

### 2017-07-29 Controller.m
Update Controller.m

@@ -30,86 +30,101 @@ func.init = @initControlSystem;
 func.run = @runControlSystem;
 end
 
+%
+% STEP #1: Modify, but do NOT rename, this function. It is called once,
+% before the simulation loop starts.
+%
 
 function [actuators,data] = initControlSystem(sensors,references,parameters,data)
 
-% Current angle of the quad (this will be passed in from the run function)
-syms ANG real
 
-% Symbolic description of A matrix
-A = [0 1 0 0 0; 0 0 0 0 parameters.g*cos(ANG); 0 0 0 1 0; ...
-    0 0 0 0 -parameters.g*sin(ANG); 0 0 0 0 0];
+data.weight = parameters.m*parameters.g;
+syms theta real
+   
+A = [0, 1, 0, 0, 0;
+     0, 0, 0, 0, parameters.g*cos(theta)/parameters.m;
+     0, 0, 0, 1, 0;
+     0, 0, 0, 0, -parameters.g*sin(theta)/parameters.m;
+     0, 0, 0, 0, 0];
 
-% Symbolic description of B matrix
-B = [0 0; 0 sin(ANG)/parameters.m; 0 0; 0 cos(ANG)/parameters.m; 1 0];
+ B = [0, 0;
+      0, sin(theta)/parameters.m;
+      0, 0;
+      0, cos(theta)/parameters.m;
+      1, 0];
 
-% Create functions
 data.funcA = matlabFunction(A);
 data.funcB = matlabFunction(B);
 
-% Initialize LQR matrices
-data.Q = 2000*eye(5);
-data.R = eye(2);
+load('optimal.mat');
+data.T = t;
+data.X = x(1,:);
+data.Xdot = x(2,:);
+data.Z = x(3,:);
+data.Zdot = x(4,:);
+data.Theta = x(5,:);
 
-% Trajectory
-load('traj.mat')
-data.trajT = t;
-data.trajX = x(1,:);
-data.trajXdot = x(2,:);
-data.trajZ = x(3,:);
-data.trajZdot = x(4,:);
-data.trajTheta = x(5,:);
-data.trajIND = 1;
 
-% Analysis variables
-data.stationaryVelocityMargin = .01; % Required velocity from rest (for both x and z)
-data.finalPositionMargin = .01; % Required distance from final position (for both x and z)
-data.endBool = 0; % Used to only display the end time once
+% Initialize
+data.index = 1;
+data.x_eq = zeros(5,1);
+data.Bool = 0;
 
-% Run the controller
[…]

### 2017-07-29 Controller.m
Tuned weight matrices for performance

@@ -48,7 +48,7 @@ data.funcA = matlabFunction(A);
 data.funcB = matlabFunction(B);
 
 % Initialize LQR matrices
-data.Q = 1000*eye(5);
+data.Q = 350*eye(5);
 data.R = eye(2);
 
 % Trajectory

### 2017-08-05 AnalysisOfOptimalTrajectory.m
Fixed controller to properly work with trajectories Added a file created by Bretl for 353 that nicely plots true trajectory against ideal trajectory Added a file (still in progress) to automate the whole process

@@ -1,0 +1,29 @@
+function AnalysisOfOptimalTrajectory
+
+load traj
+topt = t;
+xopt = x;
+uopt = u;
+
+load data
+tsim = processdata.t;
+xsim = [processdata.x; processdata.xdot; processdata.z; processdata.zdot; processdata.theta];
+usim = [controllerdata.actuators.pitchrate; controllerdata.actuators.thrust];
+
+clf;
+
+% Get MATLAB's standard list of colors
+colorList = get(gca,'ColorOrder');
+
+plot(topt,xopt,'-','linewidth',1);
+hold on;
+for i=1:size(xopt,1)
+    plot(tsim,xsim(i,:),'.','color',colorList(i,:));
+end
+
+legend('x','xdot','z','zdot','theta');
+
+xlim([topt(1) topt(end)]);
+
+
+end

### 2017-08-05 Controller.m

@@ -33,12 +33,12 @@ end
 
 function [actuators,data] = initControlSystem(sensors,references,parameters,data)
 
-% Current angle of the quad (this will be passed in from the run function)
-syms ANG real
+% Current angle of the quad and current thrust (this will be passed in from the run function)
+syms ANG THRUST real
 
 % Symbolic description of A matrix
-A = [0 1 0 0 0; 0 0 0 0 parameters.g*cos(ANG); 0 0 0 1 0; ...
-    0 0 0 0 -parameters.g*sin(ANG); 0 0 0 0 0];
+A = [0 1 0 0 0; 0 0 0 0 THRUST*cos(ANG)/parameters.m; 0 0 0 1 0; ...
+    0 0 0 0 -THRUST*sin(ANG)/parameters.m; 0 0 0 0 0];
 
 % Symbolic description of B matrix
 B = [0 0; 0 sin(ANG)/parameters.m; 0 0; 0 cos(ANG)/parameters.m; 1 0];
@@ -48,7 +48,7 @@ data.funcA = matlabFunction(A);
 data.funcB = matlabFunction(B);
 
 % Initialize LQR matrices
-data.Q = 350*eye(5);
+data.Q = 700*eye(5);
 data.R = eye(2);
 
 % Trajectory
@@ -59,6 +59,8 @@ data.trajXdot = x(2,:);
 data.trajZ = x(3,:);
 data.trajZdot = x(4,:);
 data.trajTheta = x(5,:);
+data.trajW = u(2,:);
+data.trajF = u(1,:);
 data.trajIND = 1;
 
 % Analysis variables
@@ -82,6 +84,8 @@ if (data.trajIND<length(data.trajT))
     trajZ = data.trajZ(ind);
     trajZdot = data.trajZdot(ind);
     trajTheta = data.trajTheta(ind);
+    trajW = data.trajW(ind);
+    trajF = data.trajF(ind);
 else
     data.trajIND = data.trajIND+1;
     trajX = data.trajX(end);
@@ -89,20 +93,21 @@ else
     trajZ = data.trajZ(end);
     trajZdot = data.trajZdot(end);
     trajTheta = data.trajTheta(end);
+    trajW = 0;
+    trajF = parameters.m * parameters.g;
 end
 
 % Linearize
-ANG = trajTheta;
-A = data.funcA(ANG);
-B = data.funcB(ANG);
+A = data.funcA(trajTheta,trajF);
+B = data.funcB(trajTheta);
[…]

### 2017-08-05 automate.m

@@ -1,0 +1,6 @@
+%In the future, this file should be able to decide the desired end position
+%, duration, etc. that will be imposed on every file.  Also, finding or
+%implementing an option to suspend animation of the flight may be useful
+planOptimalTrajectory()
+DesignProblemSummer2017('Controller','datafile','data.mat')
+AnalysisOfOptimalTrajectory()

### 2017-08-05 planOptimalTrajectory.m

@@ -9,6 +9,7 @@ zInitial = 0;
 xFinal = 1;
 zFinal = 0;
 m = 1;
+g = 9.81;
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 %                     Set up function handles                             %
@@ -18,7 +19,7 @@ m = 1;
 % Put symbolic EOMs in convenient form
 syms x xdot z zdot theta thrust w real
 f = simplify([xdot; (thrust/m)*sin(theta); zdot; ...
-    (thrust/m)*cos(theta) - 9.81; w]);
+    (thrust/m)*cos(theta) - g; w]);
 % Convert EOMs from symbolic to numeric
 numf = matlabFunction(f,'vars',[x xdot z zdot theta thrust w]);
 
@@ -55,7 +56,7 @@ problem.bounds.control.upp = [maxThrust; maxPitchRate];
 
 problem.guess.time = [0,duration];
 problem.guess.state = [problem.bounds.initialState.low, problem.bounds.finalState.low];
-problem.guess.control = [[0; 0],[0; 0]];
+problem.guess.control = [[0; 0],[g; 0]];
 
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%

### 2017-08-05 Papers/DroneInTheWind.tex
updated paper to reflect changes, paper needs a lot of work / rearranging / data before it is ready to be submitted

@@
 	\end{equation}
-such that $\omega$ corresponds to angular pitch rate and $f$ corresponds to thrust.
-Taking the Jacobian lends the following A and B matrices shown by Equation \ref{A_matrix_intermediate} and Equation \ref{B_matrix_intermediate}
-\begin{equation}
-\label{A_matrix_intermediate}
-A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && \frac{f\cos{\theta}}{m} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && \frac{-f\sin{\theta}}{m} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
-\end{equation}
-
-\begin{equation}
-\label{B_matrix_intermediate}
-B = \begin{bmatrix} 0 && 0 \\ 0 && \frac{\sin{\theta}}{m} \\ 0 && 0 \\ 0 && \frac{\cos{\theta}}{m} \\ 1 && 0 \end{bmatrix}
-\end{equation}
-Substituting the equilibrium force, $f = mg$, results in the following matrices shown in Equation \ref{A_matrix} and Equation \ref{B_matrix}.
+	such that $\omega$ corresponds to angular pitch rate and $f$ corresponds to thrust.  The equations of motion for the system are
+	\begin{align*}
+		\dot{x} &= \dot{x} \\
+		\ddot{x} &= \frac{f}{m}\sin\theta \\
+		\dot{z} &= \dot{z} \\
+		\ddot{z} &= \frac{f}{m}\cos\theta - g\\
+		\dot{\theta} &= \omega.
+	\end{align*}
+	Taking the Jacobian lends the following A and B matrices 
 	\begin{equation}
 		\label{A_matrix}
-A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && g\cos{\theta} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && -g\sin{\theta} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
+		A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && \frac{f\cos{\theta}}{m} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && \frac{-f\sin{\theta}}{m} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
 	\end{equation}
@@
 	\end{equation}
+
+	Which completes the linearized system.
 
@@
 	The controller is designed to use in the loop control with LQR to follow a given trajectory.
-First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ is the only variable.
+First, the init function creates a symbolic description of the A and B matrices.
 These symbolic descriptions are then turned into MATLAB functions and saved in the data struct.
@@
 	Logic is used at the start of the control loop to determine if there is still trajectory data available for the current timestep.
-If there is not, the controller will linearize about the last available trajectory point.
-This case does not happen in current simulations because the trajectory is planned for the entire duration of the simulation.
+If there is not, the controller will use the last available trajectory point for the state.
+The pitchrate and thrust will be set to $\omega = 0$ and $f = mg$, respectively.
+The reason that we cannot simply use the last available trajectory point for $\omega$ and $f$ is that the trajectory frequently does not end with the equilibrium input.
 	\newline
@@
 	\newline
-Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.
-Note here that the thrust is augmented by the equilibrium condition for hover, $f = mg$.
+	Finally, the input $u = -Kx + n$ is applied in which $u$ and $n$ are the input to be applied and the trajectory input at the current time, respectively.
 K is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.

### 2017-08-05 AnalysisOfOptimalTrajectory.m
Updated trajectory planning to be consistent with ordering of inputs, pitchrate first, thrust second Changed guess at starting control

@@ -15,13 +15,18 @@ clf;
 % Get MATLAB's standard list of colors
 colorList = get(gca,'ColorOrder');
 
-plot(topt,xopt,'-','linewidth',1);
+%plot(topt,xopt,'-','linewidth',1);
+plot(topt,uopt,'-','linewidth',1);
+
 hold on;
-for i=1:size(xopt,1)
-    plot(tsim,xsim(i,:),'.','color',colorList(i,:));
+%for i=1:size(xopt,1)
+for i=1:size(uopt,1)
+    %plot(tsim,xsim(i,:),'.','color',colorList(i,:));
+    plot(tsim,usim(i,:),'.','color',colorList(i,:));
 end
 
-legend('x','xdot','z','zdot','theta');
+%legend('x','xdot','z','zdot','theta');
+legend('pitchrate','thrust');
 
 xlim([topt(1) topt(end)]);
 

### 2017-08-05 Controller.m

@@ -59,8 +59,8 @@ data.trajXdot = x(2,:);
 data.trajZ = x(3,:);
 data.trajZdot = x(4,:);
 data.trajTheta = x(5,:);
-data.trajW = u(2,:);
-data.trajF = u(1,:);
+data.trajW = u(1,:);
+data.trajF = u(2,:);
 data.trajIND = 1;
 
 % Analysis variables

### 2017-08-05 automate.m

@@ -1,5 +1,5 @@
 %In the future, this file should be able to decide the desired end position
-%, duration, etc. that will be imposed on every file.  Also, finding or
+%, duration, timestep, etc. that will be imposed on every file.  Also, finding or
 %implementing an option to suspend animation of the flight may be useful
 planOptimalTrajectory()
 DesignProblemSummer2017('Controller','datafile','data.mat')

### 2017-08-05 planOptimalTrajectory.m

@@ -1,8 +1,8 @@
 clc; clear;
 addpath OptimTraj/
 
-maxThrust = 15;
 maxPitchRate = 5;
+maxThrust = 15;
 duration = 5;
 xInitial = 0;
 zInitial = 0;
@@ -10,6 +10,7 @@ xFinal = 1;
 zFinal = 0;
 m = 1;
 g = 9.81;
+timeDensity = 50;
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 %                     Set up function handles                             %
@@ -21,7 +22,7 @@ syms x xdot z zdot theta thrust w real
 f = simplify([xdot; (thrust/m)*sin(theta); zdot; ...
     (thrust/m)*cos(theta) - g; w]);
 % Convert EOMs from symbolic to numeric
-numf = matlabFunction(f,'vars',[x xdot z zdot theta thrust w]);
+numf = matlabFunction(f,'vars',[x xdot z zdot theta w thrust]);
 
 problem.func.dynamics = @(t,x,u)( numf(x(1,:), x(2,:), x(3,:), x(4,:), ... 
     x(5,:), u(1,:), u(2,:)) );
@@ -47,8 +48,8 @@ problem.bounds.finalState.upp = [xFinal; 0; zFinal; 0; 0];
 % problem.bounds.state.low = [-2*dist;-2*pi;-inf;-inf];
 % problem.bounds.state.upp = [2*dist;2*pi;inf;inf];
 
-problem.bounds.control.low = [0; -maxPitchRate];
-problem.bounds.control.upp = [maxThrust; maxPitchRate];
+problem.bounds.control.low = [-maxPitchRate; 0];
+problem.bounds.control.upp = [maxPitchRate; maxThrust];
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 %                    Initial guess at trajectory                          %
@@ -56,7 +57,7 @@ problem.bounds.control.upp = [maxThrust; maxPitchRate];
 
 problem.guess.time = [0,duration];
 problem.guess.state = [problem.bounds.initialState.low, problem.bounds.finalState.low];
[…]

### 2017-08-05 Controller.m
Changed thrust minimum from 0 to 1 in trajectory to prevent sparse A matrix that was causing poor tracking of trajectory Greatly increased timestep density for analysis reasons, marked with "MODIFICATION" where it was changed (it runs slowly with this many steps)

@@ -100,15 +100,33 @@ end
 % Linearize
 A = data.funcA(trajTheta,trajF);
 B = data.funcB(trajTheta);
-K = lqr(A,B,data.Q,data.R);
+data.K = lqr(A,B,data.Q,data.R);
 
 % Calculate and apply input
 state = [sensors.x; sensors.xdot; sensors.z; sensors.zdot; sensors.theta] - ...
     [trajX; trajXdot; trajZ; trajZdot; trajTheta];
-input = -K*state + [trajW; trajF];
+input = -data.K*state + [trajW; trajF];
 actuators.pitchrate = input(1);
 actuators.thrust = input(2);
 
+% %This section, when turned on, rejects saturated input; however that can
+% %negatively impact analysis, so I'm keeping it off 
+% if input(1) < -parameters.maxpitchrate;
+%     actuators.pitchrate = -parameters.maxpitchrate;
+% elseif input(1) > parameters.maxpitchrate;
+%     actuators.pitchrate = parameters.maxpitchrate;
+% else
+%     actuators.pitchrate = input(1);
+% end
+% if input(2) < 0;
+%     actuators.thrust = 0;
+% elseif input(2) > parameters.maxthrust;
+%     actuators.thrust = parameters.maxthrust;
+% else
+%     actuators.thrust = input(2);
+% end
+
+% Display when the quad has reached the goal state
 if abs(sensors.xdot) < data.stationaryVelocityMargin && ...
         abs(sensors.zdot) < data.stationaryVelocityMargin && ...
         abs(sensors.x - data.trajX(end)) < data.finalPositionMargin && ...

### 2017-08-05 DesignProblemSummer2017.m

@@ -82,7 +82,7 @@ process.tStart = 0;
 % - Stop time.
 process.tStop = 5; % MODIFICATION: Runtime
 % - Time step.
-process.tStep = 1/50;
+process.tStep = 1/500;
 % - Names of things to log in datafile, if desired
 process.processdatatolog = {'t','x','xdot','z','zdot','theta'};
 

### 2017-08-05 planOptimalTrajectory.m

@@ -3,6 +3,7 @@ addpath OptimTraj/
 
 maxPitchRate = 5;
 maxThrust = 15;
+minThrust = 1;
 duration = 5;
 xInitial = 0;
 zInitial = 0;
@@ -10,7 +11,7 @@ xFinal = 1;
 zFinal = 0;
 m = 1;
 g = 9.81;
-timeDensity = 50;
+timeDensity = 500;
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 %                     Set up function handles                             %
@@ -48,7 +49,7 @@ problem.bounds.finalState.upp = [xFinal; 0; zFinal; 0; 0];
 % problem.bounds.state.low = [-2*dist;-2*pi;-inf;-inf];
 % problem.bounds.state.upp = [2*dist;2*pi;inf;inf];
 
-problem.bounds.control.low = [-maxPitchRate; 0];
+problem.bounds.control.low = [-maxPitchRate; minThrust];
 problem.bounds.control.upp = [maxPitchRate; maxThrust];
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%

### 2017-08-05 AnalysisOfOptimalTrajectory.m
completed automate.m such that you can now modify variables across all files using it.  Note that neither the simulation nor trajectory creator will run without runOptions.mat, but this can be easily reverted if need be

@@ -15,20 +15,24 @@ clf;
 % Get MATLAB's standard list of colors
 colorList = get(gca,'ColorOrder');
 
-%plot(topt,xopt,'-','linewidth',1);
-plot(topt,uopt,'-','linewidth',1);
-
+% Comment from here (State)
+plot(topt,xopt,'-','linewidth',1);
 hold on;
-%for i=1:size(xopt,1)
-for i=1:size(uopt,1)
-    %plot(tsim,xsim(i,:),'.','color',colorList(i,:));
-    plot(tsim,usim(i,:),'.','color',colorList(i,:));
+for i=1:size(xopt,1)
+    plot(tsim,xsim(i,:),'.','color',colorList(i,:));
 end
+legend('x','xdot','z','zdot','theta');
+% To here
 
-%legend('x','xdot','z','zdot','theta');
-legend('pitchrate','thrust');
+% % Comment from here (Input)
+% plot(topt,uopt,'-','linewidth',1);
+% hold on;
+% for i=1:size(uopt,1)
+%     plot(tsim,usim(i,:),'.','color',colorList(i,:));
+% end
+% legend('pitchrate','thrust');
+% % To here
 
 xlim([topt(1) topt(end)]);
-
 
 end

### 2017-08-05 DesignProblemSummer2017.m

@@ -74,15 +74,16 @@ end
 
 function [process,controller] = SetupSimulation(process)
 
+load('runOptions')
 % DEFINE CONSTANTS
 
 % Constants related to simulation.
 % - State time.
 process.tStart = 0;
 % - Stop time.
-process.tStop = 5; % MODIFICATION: Runtime
+process.tStop = runTime; % MODIFICATION: Runtime
 % - Time step.
-process.tStep = 1/500;
+process.tStep = 1/timeDensity; % MODIFICATION: Timestep
 % - Names of things to log in datafile, if desired
 process.processdatatolog = {'t','x','xdot','z','zdot','theta'};
 

### 2017-08-05 automate.m

@@ -1,6 +1,12 @@
-%In the future, this file should be able to decide the desired end position
-%, duration, timestep, etc. that will be imposed on every file.  Also, finding or
-%implementing an option to suspend animation of the flight may be useful
+% Constants to be applied
+clear; 
+xFinal = 1;
+zFinal = 0;
+timeDensity = 500;
+runTime = 1;
+save('runOptions.mat');
+
+%Run the three scripts
 planOptimalTrajectory()
 DesignProblemSummer2017('Controller','datafile','data.mat')
 AnalysisOfOptimalTrajectory()

### 2017-08-05 planOptimalTrajectory.m

@@ -1,17 +1,14 @@
 clc; clear;
 addpath OptimTraj/
+load('runOptions')
 
 maxPitchRate = 5;
 maxThrust = 15;
 minThrust = 1;
-duration = 5;
 xInitial = 0;
 zInitial = 0;
-xFinal = 1;
-zFinal = 0;
 m = 1;
 g = 9.81;
-timeDensity = 500;
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 %                     Set up function handles                             %
@@ -39,7 +36,7 @@ problem.func.bndObj = @(t0,x0,tF,xF)(tF-t0);
 problem.bounds.initialTime.low = 0;
 problem.bounds.initialTime.upp = 0;
 problem.bounds.finalTime.low = 0;
-problem.bounds.finalTime.upp = duration;
+problem.bounds.finalTime.upp = runTime;
 
 problem.bounds.initialState.low = [xInitial; 0; zInitial; 0; 0];
 problem.bounds.initialState.upp = [xInitial; 0; zInitial; 0; 0];
@@ -56,7 +53,7 @@ problem.bounds.control.upp = [maxPitchRate; maxThrust];
 %                    Initial guess at trajectory                          %
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 
-problem.guess.time = [0,duration];
+problem.guess.time = [0,runTime];
 problem.guess.state = [problem.bounds.initialState.low, problem.bounds.finalState.low];
 problem.guess.control = [[0; g],[0; g]];
 

### 2017-08-08 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex

--- 2017-07-29 Papers/DroneInTheWind.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Controller and Optimization}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                               Controller                                                                              %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Controller}
-The controller is designed to use in the loop control with LQR to follow a given trajectory.
-First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ is the only variable.
-These symbolic descriptions are then turned into MATLAB functions and saved in the data struct.
-The Q and R weight matrices are then initialized.
-The init function proceeds to load in the trajectory data and also adds it to the data struct.
-Finally, some parameters used to determine when the quad has reached its destination are initialized.
-\newline
-\newline
-Logic is used at the start of the control loop to determine if there is still trajectory data available for the current timestep.
-If there is not, the controller will linearize about the last available trajectory point.
-This case does not happen in current simulations because the trajectory is planned for the entire duration of the simulation.
-\newline
-\newline
-After determining that the simulation is still within the regime in which a trajectory is available, the controller will find the respective trajectory point to linearize about for the current timestep.
-The angle for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
-\newline
-\newline
-Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.
-Note here that the thrust is augmented by the equilibrium condition for hover, $f = mg$.
-K is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.
+\section{Optimization and Controller}
 
@@
 
+The optimal trajectory can now be solved for and subsequently "unpacked".
+By unpacking the solution, the state and input over time can be tracked and analyzed.
+One thing to note, however, is that the time-steps of solution matrices do \textbf{not} line up with the simulation that will run the controller with the optimal trajectory.
+This can be mitigated in the OptimTraj solver options, but will still lead to errors, which will be discussed further below.
 \subsubsection{Function Dynamics}
@@
 \subsubsection{Problem Bounds}
-The next step is to set up the \lstinline!problem.func.dynamics!. For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in \textbf{Table 1} below. 
+The next step is to set up the \lstinline!problem.bounds!.
+For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in \textbf{Table 1} below.
+These parameters were chosen so that results of the simulation can be compared to D'Andrea's paper, \textit{Performance benchmarking of quadrotor systems using time-optimal control}.
+\textcolor{red}{Citation}
 \begin{figure}[H]
@@
  $t_{i}$   & 0 s  & Initial time\\
- $t_{f}$  & 5 s  & Final time\\
+ $t_{f}$  & 2 s  & Final time\\
  $\underline{F}/m$ & 0 m/$s^{2}$ & Min thrust\\
- $\overline{F}/m$ & 15 m/$s^{2}$ & Max thrust\\
- $\overline{\omega}$ & 5 rad/s & Max pitch rate \\
+ $\overline{F}/m$ & 20 m/$s^{2}$ & Max thrust\\
+ $\overline{\omega}$ & 10 rad/s & Max pitch rate \\
  \hline
@@
 
+% time objective function for boundary points
+problem.func.bndObj = @(t0,x0,tF,xF) (tF-t0)
+
 \end{lstlisting}
@@
 \subsubsection{Options}
-Additional options are available using \lstinline!problem.options!, which include details to change accuracy settings and select different solution methods.
-Different methods include trapezoid, Hermite Simpson, Chebyshev, and the Runge Kutta method.
+Additional options are available using \lstinline!problem.options!, which include details to change accuracy settings and select different solution methods, like trapezoid, Chebyshev, etc.
 \subsubsection{Solution}
 Finally, running the command \lstinline!soln = optimTraj(problem)! is used to solve. Following this, it is possible to unpack the simulation, save the data, and plot out.
+\begin{quote}
+\begin{lstlisting}
+t = linspace(soln.grid.time(1),soln.grid.time(end),soln.grid.time(end)*TimeDensity);
+x = soln.interp.state(t);
+u = soln.interp.control(t);
+save('traj.mat','t','x','u');
+\end{lstlisting}
+\end{quote}
+
+The reason the time grid-spacing is the end-time multiplied by \lstinline!TimeDesnity!
+is to keep the grid-spacing of the simulation and optimal trajectory path the same.
+This will be elaborated on a further in \textcolor{red}{Section 4, \textbf{Running Simulation}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                               Controller                                                                              %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Controller}
+The controller is designed to use in the loop control with LQR to follow a given trajectory.
+First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ is the only variable.
+These symbolic descriptions are then turned into MATLAB functions and saved in the data struct.
+The Q and R weight matrices are then initialized.
+The init function proceeds to load in the trajectory data and also adds it to the data struct.
+Finally, some parameters used to determine when the quad has reached its destination are initialized.
+\begin{quote}
+\begin{lstlisting}
+% Create functions
+data.funcA = matlabFunction(A);
+data.funcB = matlabFunction(B);
+
+% Trajectory
+load('traj.mat')
+\end{lstlisting}
+\end{quote}
+
+Logic is used at the start of the control loop to determine if there is still trajectory data available for the current timestep.
+If there is not, the controller will linearize about the last available trajectory point.
+This case does not happen in current simulations because the trajectory is planned for the entire duration of the simulation.
+\begin{quote}
+\begin{lstlisting}
+% Create functions
+if data.index <= length(data.T)
+    data.x_eq = [data.X(data.index);
+                 data.Xdot(data.index);
+                 data.Z(data.index);
+                 data.Zdot(data.index);
+                 data.Theta(data.index)];
+
+    data.index = data.index + 1;
+end
+
+\end{lstlisting}
+\end{quote}
+Where \lstinline!data.index!
+is initialized at 1.
+Recall, however, that this leads to an error.
+Fortunately, the states of each index are close enough to the quadcopter's actual state that it will still converge and follow a similar path to the time-optimal trajectory.
+\newline
+\newline
+After determining that the simulation is still within the regime in which a trajectory is available, the controller will find the respective trajectory point to linearize about for the current time-step.
+The angle for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
+\begin{quote}
+\begin{lstlisting}
+theta = data.x_eq(5,1);
+A = data.funcA(theta);
+B = data.funcB(theta);
+
+\end{lstlisting}
+\end{quote}
+
+Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.
+Note here that the thrust is augmented by the equilibrium condition for hover, $f = mg$.
+K is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         Running Simulation                                                                                %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Running Simulation}
+
+To run the simulation, a function named \lstinline!automation.m! was used to set up the problem bounds, plan the optimal trajectory, and analyze the results. Below is shown the script to do so.
+\begin{quote}
+\begin{lstlisting}
+% Constants to be applied
+clear;
+
+TimeDensity = 400;
+xFinal = 5;
+zFinal = 5;
+runTime = 2;
+
+gravity = 9.81;
+mass = 1;
+
+maxPitchRate = 10;
+maxThrust = 20;
+minThrust = 1;
+
+save('runOptions.mat');
+
+%Run the three scripts
+planOptimalTrajectory()
+DesignProblemSummer2017('Controller','datafile','data.mat')
+AnalysisOfOptimalTrajectory()
+
+\end{lstlisting}
+\end{quote}
+\lstinline!TimeDensity!
+refers to the grid-spacing in the optimal trajectory solution as well as the time-step for \lstinline!DesignProblemSummer2017!.
+The other options set problem bounds and save them into \lstinline!runOptions.mat!
+to be used by the DesignProblem, controller, and the Optimal trajectory planner.
+\newline
+\newline
+\lstinline!AnalysisOfOptimalTrajectory()!
+plots the simulation against the optimal trajectory calculated by optimTraj.
+\textbf{Solid lines} are to show the optimal trajectory, and \textbf{dashed lines} show the simulated quad-rotor path.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Analysis}
-A method that computes quadcopter trajectories satisfying the minimal principle with respect to time-optimality has been developed.
+\section{Analysis of Optimal Trajectory}
+
+OptimTraj  was used to find the time-optimal trajectory for 5 different paths, all starting at the origin. 
+Namely, the 5 paths ended at (1,1), (2,2), (3,3), (4,4), and (5,5).
+This is so that we can see how the model actually changes behaviors over these different paths.
+Ultimately, the results will be compared to \textbf{one} of D'Andrea's results \textcolor{red}{Citation Needed}, which took the path from (0,0) to (5,5).
+All plots will be shown alongside D'Andrea's for comparison.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                                OptimTraj  Analysis                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{OptimTraj Analysis}
+\begin{quote}
+\begin{lstlisting}
+load('traj.mat')
+t = t;
+x = x(1,:);
+xd= x(2,:);
+z = x(3,:);
+zd= x(4,:);
+th= x(5,:);
+w = u(1,:);
+f = u(2,:);
+\end{lstlisting}
+\end{quote}
+The values for all 5 instances were unpacked and subsequently plotted over time.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                                Simulation Analysis                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Simulation Analysis}
+\begin{quote}
+\begin{lstlisting}
+load('data1.mat')
+t = processdata.t;
+x = processdata.x;
+xd = processdata.xdot;
+z = processdata.z;
+zd = processdata.zdot;
+th = processdata.theta;
+f = controllerdata.actuators.thrust;
+w = controllerdata.actuators.pitchrate;
+\end{lstlisting}
+\end{quote}
+Similarly, the simulations were also unpacked and plotted over time.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                              D'Andrea Results                                                                        %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{D'Andrea Results}
+
+Before comparing results to D'Andrea's of time optimal trajectory results, the differences in simulations must be addressed.
+To start, D'Andrea's control input is bang-bang in thrust and bang-singular in pitch rate.\textcolor{red}{Citation Needed}.
+Additionally, those inputs are non-zero values at both the start and end.
+Whereas our controller is continuous(\textcolor{red}{???}) and the inputs both begin at zero values.
+The plot for his results are shown in figure \textcolor{red}{X} below.
+\begin{figure}[H]
+\centerline{\includegraphics[width=12cm, height=12cm]{DAndrea_55_Plot.png}}
+  \caption{\textcolor{red}{Screenshot?}}
+  \label{fig}
+\end{figure}
+Qualitatively, the inputs can be broken down into sections, as is described by the switching functions \textcolor{red}{Let's try and get another source about this topic}.
+The Thrust begins at $20 N$, then drops to 0 as the quad-copter nears it's final state, $x=z=5$.
+The pitch rate begins at $10 rad/s$, drops to $0$, then to $-10 rad/s$ to stabilize, and finally jumps to $10 rad/s$.
+\newline
+\newline
+In the following subsections we will show how the behavior of our controller compares and how it changes as the final state goes from $x=z=1$ to $x=z=5$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                              D'Andrea Results                                                                        %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% A method that computes quadcopter trajectories satisfying the minimal principle with respect to time-optimality has been developed.
 The method is based on the two-dimensional quadcopter model with an optimal trajectory created using OptimTraj.

### 2017-08-08 Controller.m
Add files via upload

@@ -37,18 +37,24 @@ function [actuators,data] = initControlSystem(sensors,references,parameters,data
 syms ANG THRUST real
 
 % Symbolic description of A matrix
-A = [0 1 0 0 0; 0 0 0 0 THRUST*cos(ANG)/parameters.m; 0 0 0 1 0; ...
-    0 0 0 0 -THRUST*sin(ANG)/parameters.m; 0 0 0 0 0];
+A = [0 1 0 0 0; 
+     0 0 0 0 THRUST*cos(ANG)/parameters.m; 
+     0 0 0 1 0; 
+     0 0 0 0 -THRUST*sin(ANG)/parameters.m; 
+     0 0 0 0 0];
 
 % Symbolic description of B matrix
-B = [0 0; 0 sin(ANG)/parameters.m; 0 0; 0 cos(ANG)/parameters.m; 1 0];
+B = [0 0; 
+     0 sin(ANG)/parameters.m; 
+     0 0; 0 cos(ANG)/parameters.m; 
+     1 0];
 
 % Create functions
 data.funcA = matlabFunction(A);
 data.funcB = matlabFunction(B);
 
 % Initialize LQR matrices
-data.Q = 700*eye(5);
+data.Q = 200*eye(5);
 data.R = eye(2);
 
 % Trajectory
@@ -61,12 +67,17 @@ data.trajZdot = x(4,:);
 data.trajTheta = x(5,:);
 data.trajW = u(1,:);
 data.trajF = u(2,:);
-data.trajIND = 1;
+data.index = 1;
+
+load('runOPtions.mat')
+data.minThrust = minThrust;
+data.maxThrust = maxThrust;
+data.maxPitchRate = maxPitchRate;
 
 % Analysis variables
-data.stationaryVelocityMargin = .01; % Required velocity from rest (for both x and z)
-data.finalPositionMargin = .01; % Required distance from final position (for both x and z)
-data.endBool = 0; % Used to only display the end time once
+data.vel_error = .05;  % Required velocity from rest (for both x and z)
+data.pos_error = .05;  % Required distance from final position (for both x and z)
+data.endBool = 0;      % Used to only display the end time once
 
 % Run the controller
 [actuators,data] = runControlSystem(sensors,references,parameters,data);
@@ -76,9 +87,10 @@ end
 function [actuators,data] = runControlSystem(sensors,references,parameters,data)
 
 % Reference trajectory
-ind = data.trajIND;
[…]

### 2017-08-08 DesignProblemSummer2017.m

@@ -89,13 +89,15 @@ process.processdatatolog = {'t','x','xdot','z','zdot','theta'};
 
 % Constants related to physical properties.
 % - Acceleration of gravity.
-process.g = 9.81;
+process.g = gravity;
 % - Mass
-process.m = 1.0;
+process.m = mass;
 % - Maximum thrust
-process.maxthrust = 15;
+process.maxthrust = maxThrust;
+% - Minimum thrust
+process.minthrust = minThrust;
 % - Maximum pitch rate
-process.maxpitchrate = 5;
+process.maxpitchrate = maxPitchRate;
 % - Geometry
 process.sparLength = 0.5;
 process.sparWidth = 0.01;
@@ -192,18 +194,18 @@ u = [actuators.pitchrate; actuators.thrust];
 u = zeros(2,1);
 
 % Copy pitch rate from actuators
-if actuators.pitchrate<-process.maxpitchrate
+if actuators.pitchrate < -process.maxpitchrate
     u(1) = -process.maxpitchrate;
-elseif actuators.pitchrate>process.maxpitchrate
+elseif actuators.pitchrate > process.maxpitchrate
     u(1) = process.maxpitchrate;
 else
     u(1) = actuators.pitchrate;
 end
 
 % Copy thrust from actuators
-if actuators.thrust<0
-    u(2) = 0;
-elseif actuators.thrust>process.maxthrust
+if actuators.thrust<process.minthrust
+    u(2) = process.minthrust;
+elseif actuators.thrust > process.maxthrust
     u(2) = process.maxthrust;
 else
     u(2) = actuators.thrust;

### 2017-08-08 automate.m

@@ -1,9 +1,18 @@
 % Constants to be applied
 clear; 
-xFinal = 1;
-zFinal = 0;
-timeDensity = 500;
-runTime = 1;
+xFinal = 5;
+zFinal = 5;
+timeDensity = 400;
+runTime = 2;
+
+
+gravity = 9.81;
+mass = 1;
+
+maxPitchRate = 10;
+maxThrust = 20;
+minThrust = 1;
+
 save('runOptions.mat');
 
 %Run the three scripts

### 2017-08-08 planOptimalTrajectory.m

@@ -2,13 +2,10 @@ clc; clear;
 addpath OptimTraj/
 load('runOptions')
 
-maxPitchRate = 5;
-maxThrust = 15;
-minThrust = 1;
 xInitial = 0;
 zInitial = 0;
-m = 1;
-g = 9.81;
+m = mass;
+g = gravity;
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 %                     Set up function handles                             %
@@ -17,15 +14,34 @@ g = 9.81;
 
 % Put symbolic EOMs in convenient form
 syms x xdot z zdot theta thrust w real
-f = simplify([xdot; (thrust/m)*sin(theta); zdot; ...
-    (thrust/m)*cos(theta) - g; w]);
+f = simplify([xdot; 
+              (thrust/m)*sin(theta); 
+              zdot; 
+              (thrust/m)*cos(theta) - g; 
+              w]);
 % Convert EOMs from symbolic to numeric
 numf = matlabFunction(f,'vars',[x xdot z zdot theta w thrust]);
 
-problem.func.dynamics = @(t,x,u)( numf(x(1,:), x(2,:), x(3,:), x(4,:), ... 
-    x(5,:), u(1,:), u(2,:)) );
-%problem.func.pathObj = @(t,x,u)( sum((x(1,:)-xFinal).^2,1) + sum((x(3,:)-zFinal).^2,1) );
-%problem.func.pathObj = @(t,x,u)( sum(u.^2,1) );
+problem.func.dynamics = @(t,x,u)( numf(x(1,:), x(2,:), x(3,:), x(4,:), x(5,:),... 
+                                       u(1,:), u(2,:)) );
+                                   
+                                   
+                                   
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%          
+%                           Optimize for:                                     %
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
+
+% Input:
+%	problem.func.pathObj = @(t,x,u)( sum(u.^2,1) );
+
[…]

### 2017-08-08 AnalysisOfOptimalTrajectory.m
Add files via upload

@@ -1,5 +1,5 @@
 function AnalysisOfOptimalTrajectory
-
+close all
 load traj
 topt = t;
 xopt = x;
@@ -22,18 +22,20 @@ hold on;
 for i=1:size(xopt,1)
     plot(tsim,xsim(i,:),'--','color',colorList(i,:));
 end
+title('Quadcoper State')
 legend('x','xdot','z','zdot','theta');
 grid on
 % To here
 
-figure(2)
 % Comment from here (Input)
+figure(2)
 plot(topt,uopt,'-','linewidth',1);
 hold on;
 for i=1:size(uopt,1)
     plot(tsim,usim(i,:),'--','color',colorList(i,:));
 end
 legend('pitchrate','thrust');
+title('Quadcopter Inputs')
 grid on
 % To here
 

### 2017-08-09 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex

@@
 
-OptimTraj  was used to find the time-optimal trajectory for 5 different paths, all starting at the origin. 
-Namely, the 5 paths ended at (1,1), (2,2), (3,3), (4,4), and (5,5).
-This is so that we can see how the model actually changes behaviors over these different paths.
-Ultimately, the results will be compared to \textbf{one} of D'Andrea's results \textcolor{red}{Citation Needed}, which took the path from (0,0) to (5,5).
-All plots will be shown alongside D'Andrea's for comparison.
+In this section, the trajectory for $x=5,z=5$ was analyzed.
+First the Optimal trajectory was calculated and saved, then the simulation was run and data stored, and finally both results were plotted against each other.
+To reiterate, \textbf{Solid lines} are to show the optimal trajectory, and \textbf{dashed lines} show the simulated quad-rotor path.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                                OptimTraj  Analysis                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{OptimTraj Analysis}
-\begin{quote}
-\begin{lstlisting}
-load('traj.mat')
-t = t;
-x = x(1,:);
-xd= x(2,:);
-z = x(3,:);
-zd= x(4,:);
-th= x(5,:);
-w = u(1,:);
-f = u(2,:);
-\end{lstlisting}
-\end{quote}
-The values for all 5 instances were unpacked and subsequently plotted over time.
+Ultimately, the results will be compared to \textbf{one} of D'Andrea's results \textcolor{red}{Citation Needed}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{lstlisting}
-load('data1.mat')
-t = processdata.t;
-x = processdata.x;
-xd = processdata.xdot;
-z = processdata.z;
-zd = processdata.zdot;
-th = processdata.theta;
-f = controllerdata.actuators.thrust;
-w = controllerdata.actuators.pitchrate;
+load traj
+topt = t;
+xopt = x;
+uopt = u;
+
+load data
+tsim = processdata.t;
+xsim = [processdata.x; processdata.xdot; processdata.z; processdata.zdot;    processdata.theta];
+usim = [controllerdata.actuators.pitchrate;...
+	controllerdata.actuators.thrust];
 \end{lstlisting}
 \end{quote}
-Similarly, the simulations were also unpacked and plotted over time.
+The preceding lines of code are meant to show how easily the data can be unpacked and plotted against each other.
+Below, \textcolor{blue}{\textbf{Figure X} shows the optimal and actual state of the quadrotor and \textbf{figure Y} shows the optimal and actual inputs of the quadrotor.}
+
+\begin{figure}[h!]
+  \centering
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{State.png}
+    \caption{Quadcopter state over time.}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{Inputs.png}
+    \caption{Quadcopter Inputs over time.}
+  \end{minipage}
+\end{figure}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                              D'Andrea Results                                                                        %
+%                                                          Comparison with D'Andrea Results                %
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{D'Andrea Results}
+\subsection{Comparison with D'Andrea Results}
+
+We can compare the simulated trajectory with that of \textit{Performance benchmarking of quadrotor systems using time-optimal control}. \textcolor{red}{Citation}
 

### 2017-08-14 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex

@@
 \usepackage{enumitem}
+\usepackage[export]{adjustbox}
 \setlist{nosep,after=\vspace{\baselineskip}}
@@
 For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in \textbf{Table 1} below.
-These parameters were chosen so that results of the simulation can be compared to D'Andrea's paper, \textit{Performance benchmarking of quadrotor systems using time-optimal control}.
-\textcolor{red}{Citation}
+These parameters were chosen so that results of the simulation can be compared to results from D'Andrea's paper\cite{D'Andrea}.
 \begin{figure}[H]
@@
 is to keep the grid-spacing of the simulation and optimal trajectory path the same.
-This will be elaborated on a further in \textcolor{red}{Section 4, \textbf{Running Simulation}}
+This will be elaborated on a further in Section \ref{Running Simulation}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Running Simulation}
+\section{Running Simulation}\label{Running Simulation}
 
@@
 
-Ultimately, the results will be compared to \textbf{one} of D'Andrea's results \textcolor{red}{Citation Needed}.
+Ultimately, the results will be compared to \textbf{one} of D'Andrea's results\cite{D'Andrea}.
 
@@
 The preceding lines of code are meant to show how easily the data can be unpacked and plotted against each other.
-Below, \textcolor{blue}{\textbf{Figure X} shows the optimal and actual state of the quadrotor and \textbf{figure Y} shows the optimal and actual inputs of the quadrotor.}
+Below, Figure \ref{State Plot} shows the optimal and actual state of the quadrotor, and Figure \ref{Input Plot} shows the optimal and actual inputs of the quadrotor.
 
@@
   \centering
-  \begin{minipage}[b]{0.45\textwidth}
+  \begin{minipage}[b]{0.5\textwidth}
     \includegraphics[width=\textwidth]{State.png}
-    \caption{Quadcopter state over time.}
+    \caption{\label{State Plot} Quadcopter state over time.}
   \end{minipage}
@@
     \includegraphics[width=\textwidth]{Inputs.png}
-    \caption{Quadcopter Inputs over time.}
+    \caption{\label{Input Plot} Quadcopter Inputs over time.}
   \end{minipage}
 \end{figure}
+
+% \begin{figure}[H]
+%   \centering
+
+%     \includegraphics[width=.6\textwidth,left]{State.png}
+%     \label{State}
+%     \caption{\label{State Plot} Quadcopter state over time.}
+%   \end{figure}
+%   \hfill
+% \begin{figure}[H]
+% \label{Input Plot}
+%     \includegraphics[width=\textwidth]{Inputs.png}
+%     \label{Input Plot}
+%     \caption{\label{Input Plot} Quadcopter Inputs over time.}
+% \end{figure}
 
@@
 \centerline{\includegraphics[width=12cm, height=12cm]{DAndrea_55_Plot.png}}
-  \caption{\textcolor{red}{Screenshot?}}
+  \caption{\label{D'Andrea Plot} Screenshot of results}
   \label{fig}
@@
 \\\texttt{https://github.com/MatthewPeterKelly/OptimTraj}
+
+\bibitem{D'Andrea}
+D'Andrea
+
 \end{thebibliography}

### 2017-08-15 AnalysisOfOptimalTrajectory.m
Add files via upload

@@ -22,8 +22,11 @@ hold on;
 for i=1:size(xopt,1)
     plot(tsim,xsim(i,:),'--','color',colorList(i,:));
 end
+xlim([0, topt(end)])
 title('Quadcoper State')
-legend('x','xdot','z','zdot','theta');
+legend('x (m)','xdot (m/s)','z (m)','zdot (m/s)','theta (rad)','Location','northwest');
+xlabel('time (s)')
+ylabel('Magnitude')
 grid on
 % To here
 
@@ -34,8 +37,10 @@ hold on;
 for i=1:size(uopt,1)
     plot(tsim,usim(i,:),'--','color',colorList(i,:));
 end
-legend('pitchrate','thrust');
+legend('pitchrate (\omega/s)','thrust (N)','Location','northwest');
 title('Quadcopter Inputs')
+xlabel('time (s)')
+ylabel('Magnitude')
 grid on
 % To here
 

### 2017-08-15 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex

@@
 By unpacking the solution, the state and input over time can be tracked and analyzed.
-One thing to note, however, is that the time-steps of solution matrices do \textbf{not} line up with the simulation that will run the controller with the optimal trajectory.
-This can be mitigated in the OptimTraj solver options, but will still lead to errors, which will be discussed further below.
+One thing to note, however, is that the time-steps of solver matrices do \textbf{not} line up with the simulation time steps provided that run the controller.
+This is accounted for by modifying the simulation parameters.
 \subsubsection{Function Dynamics}
@@
 problem.func.dynamics= @(t,x,u) numf( x(1,:),x(2,:),x(3,:),x(4,:),x(5,:),
-                                      u(1,:), u(2,:)) );
+                                      u(1,:),u(2,:)) );
 
@@
 The next step is to set up the \lstinline!problem.bounds!.
-For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in \textbf{Table 1} below.
+For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in table \ref{Problem Bounds} below.
 These parameters were chosen so that results of the simulation can be compared to results from D'Andrea's paper\cite{D'Andrea}.
-\begin{figure}[H]
+
+\begin{table}[H]
 \begin{center}
 \begin{tabular}{ |p{2.5cm}||p{2cm}||p{3cm}| }
- \hline
- \multicolumn{3}{|c|}{\textbf{Table 1}   Problem Bounds} \\
+
  \hline
@@
  $t_{f}$  & 2 s  & Final time\\
- $\underline{F}/m$ & 0 m/$s^{2}$ & Min thrust\\
+ $\underline{F}/m$ & 1 m/$s^{2}$ & Min thrust\\
  $\overline{F}/m$ & 20 m/$s^{2}$ & Max thrust\\
@@
 \end{tabular}
+\caption{Problem Bounds }
+\label{Problem Bounds}
 \end{center}
-\end{figure}
+\end{table}
 
@@
 
-% time
+% Time
 problem.func.pathObj = @(t,x,u)( sum((x(1,:)-x_f).^2,1) 
@@
 
-% time objective function for boundary points
+% Time objective function for boundary points
 problem.func.bndObj = @(t0,x0,tF,xF) (tF-t0)
@@
 \end{quote}
-Where \lstinline!data.index!
-is initialized at 1.
-Recall, however, that this leads to an error.
-Fortunately, the states of each index are close enough to the quadcopter's actual state that it will still converge and follow a similar path to the time-optimal trajectory.
+Where \lstinline!data.index! is initialized at 1. 
 \newline
@@
 Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.
-Note here that the thrust is augmented by the equilibrium condition for hover, $f = mg$.
+Note here that for hover, the thrust \textit{must} augmented by the equilibrium condition, $f = mg$.
 K is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                                Analysis                                                                                %
+%                                                                                Analysis  of Optimal Trajectory  %
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Below, Figure \ref{State Plot} shows the optimal and actual state of the quadrotor, and Figure \ref{Input Plot} shows the optimal and actual inputs of the quadrotor.
+\newline
+\newline
+Reminder, \textbf{Solid lines} show the calculated optimal trajectory. \textbf{Dashed lines} show the simulated quad-rotor path.
 
@@
 
-% \begin{figure}[H]
-%   \centering
-
-%     \includegraphics[width=.6\textwidth,left]{State.png}
-%     \label{State}
-%     \caption{\label{State Plot} Quadcopter state over time.}
-%   \end{figure}
-%   \hfill
-% \begin{figure}[H]
-% \label{Input Plot}
-%     \includegraphics[width=\textwidth]{Inputs.png}
-%     \label{Input Plot}
-%     \caption{\label{Input Plot} Quadcopter Inputs over time.}
-% \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We can compare the simulated trajectory with that of \textit{Performance benchmarking of quadrotor systems using time-optimal control}. \textcolor{red}{Citation}
+We can compare the simulated trajectory with that of \textit{Performance Benchmarking of Quadrotor Systems Using Time-Optimal Control} \cite{D'Andrea}.
+The trajectory to be compared to from D'Andrea's paper is shown in Figure \ref{D'Andrea Plot}
 
-Before comparing results to D'Andrea's of time optimal trajectory results, the differences in simulations must be addressed.
-To start, D'Andrea's control input is bang-bang in thrust and bang-singular in pitch rate.\textcolor{red}{Citation Needed}.
-Additionally, those inputs are non-zero values at both the start and end.
-Whereas our controller is continuous(\textcolor{red}{???}) and the inputs both begin at zero values.
-The plot for his results are shown in figure \textcolor{red}{X} below.
 \begin{figure}[H]
-\centerline{\includegraphics[width=12cm, height=12cm]{DAndrea_55_Plot.png}}
-  \caption{\label{D'Andrea Plot} Screenshot of results}
+\centerline{\includegraphics[width=9cm, height=8.5cm]{DAndrea_55_Plot.png}}
+  \caption{\label{D'Andrea Plot} Screenshot of D'Andrea Results}
   \label{fig}
 \end{figure}
-Qualitatively, the inputs can be broken down into sections, as is described by the switching functions \textcolor{red}{Let's try and get another source about this topic}.
-The Thrust begins at $20 N$, then drops to 0 as the quad-copter nears it's final state, $x=z=5$.
-The pitch rate begins at $10 rad/s$, drops to $0$, then to $-10 rad/s$ to stabilize, and finally jumps to $10 rad/s$.
-\newline
-\newline
-In the following subsections we will show how the behavior of our controller compares and how it changes as the final state goes from $x=z=1$ to $x=z=5$.
+
+Though both results are nearly identical, the biggest difference in performance is in that of the inputs. 
+D'Andrea input for thrust is bang-bang, meaning there is a switch discontinuity AND the input only takes the minimum and maximum values \cite{BangBangControl}.
+D'Andrea's pitch rate is bang-singular, meaning the control input is always at full positive or negative saturation, except during singular arcs \cite{D'Andrea}.
+
+In our model, the inputs were free to vary as continuously as possible between the bounds set in table \ref{Problem Bounds}.
+Despite this, both models arrived at the destination $x=z=5$ following the same time-optimal path and input behavior.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% A method that computes quadcopter trajectories satisfying the minimal principle with respect to time-optimality has been developed.
-The method is based on the two-dimensional quadcopter model with an optimal trajectory created using OptimTraj.
-By defining the dynamics, bounds and cost function the algorithm was able to create an optimal path for which the drone was to follow.
-Testing this method, the simulated drone accomplished moving from a position (0,0) to (1,1) in a time optimal manner.
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{itemize}
-With these immediate goals in mind, an accurate simulation can be created to further test the overarching research initiative.
+\textit{Controlling of an Single Drone}\cite{Controlling of an Single Drone} provides an outline for how to linearize a 3D quadcopter using rigid body dynamics.
+A key difference to note is that in the dynamics discussed in \cite{Controlling of an Single Drone}, each of the four quadrotor blades can produce its own thrust, which will then control the pitch, roll, and yaw of the rigid body.
+Additionally, the paper gives a brief description of the mechanism on applying aerodynamic forces, namely, drag.
+
 % Display list of references in IEEE Transactions format.
@@
 % Display list of references in IEEE format.
+
 \begin{thebibliography}{9}
+
+\bibitem{Controlling of an Single Drone}
+Emile Biever
+\textit{Controlling of an Single Drone}.
+TU/E Eindhoven: Department of Mechanical Engineering, 2015.
+
 \bibitem{OptimTraj} 
-MatthewPeterKelly
+Matthew Peter Kelly
 \textit{OptimTraj}
@@
 
+\bibitem{BangBangControl}
+Nguyen Tan Tien
+\textit{Introduction to Control Theory Including Optimal Control}.
+C.11 Bang-bang Control:53-58, 2002
+\\\texttt{https://goo.gl/pj9oyA}
+% Too long to fit:
+%  http://www4.hcmut.edu.vn/~nttien/Lectures/Optimal%20Control/C.11%20Bang-bang%20Control.pdf
+
 \bibitem{D'Andrea}
-D'Andrea
+Rafaello D'Andrea
+\textit{Performance Benchmarking of Quadrotor Systems Using Time-Optimal Control}.
+Auton Robot, 33:69-88, 2012.
 

### 2017-08-15 AnalysisOfOptimalTrajectory.m
Add files via upload

@@ -22,13 +22,12 @@ hold on;
 for i=1:size(xopt,1)
     plot(tsim,xsim(i,:),'--','color',colorList(i,:));
 end
-xlim([0, topt(end)])
 title('Quadcoper State')
-legend('x (m)','xdot (m/s)','z (m)','zdot (m/s)','theta (rad)','Location','northwest');
+legend('x (m)','xdot (m/s)','z (m)','zdot (m/s)','theta (rad)');
 xlabel('time (s)')
-ylabel('Magnitude')
 grid on
 % To here
+xlim([topt(1) topt(end)]);
 
 % Comment from here (Input)
 figure(2)
@@ -37,10 +36,9 @@ hold on;
 for i=1:size(uopt,1)
     plot(tsim,usim(i,:),'--','color',colorList(i,:));
 end
-legend('pitchrate (\omega/s)','thrust (N)','Location','northwest');
+legend('pitchrate (rad/s)','thrust (N)','location','northwest');
 title('Quadcopter Inputs')
 xlabel('time (s)')
-ylabel('Magnitude')
 grid on
 % To here
 

### 2017-08-15 AnalysisOfOptimalTrajectory.m
Update AnalysisOfOptimalTrajectory.m

@@ -23,7 +23,7 @@ for i=1:size(xopt,1)
     plot(tsim,xsim(i,:),'--','color',colorList(i,:));
 end
 title('Quadcoper State')
-legend('x (m)','xdot (m/s)','z (m)','zdot (m/s)','theta (rad)');
+legend('x (m)','xdot (m/s)','z (m)','zdot (m/s)','theta (rad)','location','northwest');
 xlabel('time (s)')
 grid on
 % To here

### 2017-08-16 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex
paper updates

@@
 % Say where pictures (if any) will be placed
-\graphicspath{{./pictures/}}
+\graphicspath{{./Pictures/}}
 
@@
 	\end{equation}
-Substituting the equilibrium force, $f = mg$, results in the following matrices shown in Equation \ref{A_matrix} and Equation \ref{B_matrix}.
-\begin{equation}
-\label{A_matrix}
-A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && g\cos{\theta} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && -g\sin{\theta} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
-\end{equation}
-
-\begin{equation}
-\label{B_matrix}
-B = \begin{bmatrix} 0 && 0 \\ 0 && \frac{\sin{\theta}}{m} \\ 0 && 0 \\ 0 && \frac{\cos{\theta}}{m} \\ 1 && 0 \end{bmatrix}
-\end{equation}
+	There is no need to substitute in equilibrium conditions because we will be linearizing about a trajectory.
 
@@
 	OptimTraj \cite{OptimTraj} was used for trajectory planning.
-OptiTraj is a MATLAB library designed by a Cornell PHD student, Matthew P.
+OptimTraj is a MATLAB library designed by a Cornell PHD student, Matthew P.
 Kelly, to solve for continuous-time single-phase trajectory optimization problems.
@@
 	\subsubsection{Solution}
-Finally, running the command \lstinline!soln = optimTraj(problem)! is used to solve. Following this, it is possible to unpack the simulation, save the data, and plot out.
+	Finally, running the command \lstinline!soln = optimTraj(problem)! is used to solve. Following this, it is possible to unpack the simulation, save the data, and plot it.
 	\begin{quote}
@@
 	The controller is designed to use in the loop control with LQR to follow a given trajectory.
-First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ is the only variable.
+First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ and the thrust $f$ are the only variables.
 These symbolic descriptions are then turned into MATLAB functions and saved in the data struct.
@@
 If there is not, the controller will linearize about the last available trajectory point.
-This case does not happen in current simulations because the trajectory is planned for the entire duration of the simulation.
 	\begin{quote}
@@
 	After determining that the simulation is still within the regime in which a trajectory is available, the controller will find the respective trajectory point to linearize about for the current time-step.
-The angle for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
+The angle and thrust for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
 	\begin{quote}
@@
 
-Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.
-Note here that for hover, the thrust \textit{must} augmented by the equilibrium condition, $f = mg$.
-K is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.
+	Finally, the input $u = -Kx + n$ is applied in which $K$ is the previously specified gain matrix, $x$ is the difference between the current state and the trajectory state at the current time, and $n$ is the trajectory input at the current time.
 
@@
 
-To run the simulation, a function named \lstinline!automation.m! was used to set up the problem bounds, plan the optimal trajectory, and analyze the results. Below is shown the script to do so.
+	To run the simulation, a function named \lstinline!automation.m! was used to set up the problem bounds, plan the optimal trajectory, and analyze the results. Shown below is the script to do so.
 	\begin{quote}
@@
 		\centering
-  \begin{minipage}[b]{0.5\textwidth}
+		\begin{minipage}[b]{0.49\textwidth}
 			\includegraphics[width=\textwidth]{State.png}
@@
 		\hfill
-  \begin{minipage}[b]{0.45\textwidth}
+		\begin{minipage}[b]{0.49\textwidth}
 			\includegraphics[width=\textwidth]{Inputs.png}
@@
 	Though both results are nearly identical, the biggest difference in performance is in that of the inputs. 
-D'Andrea input for thrust is bang-bang, meaning there is a switch discontinuity AND the input only takes the minimum and maximum values \cite{BangBangControl}.
+	D'Andrea input for thrust is bang-bang, meaning there is a switch discontinuity and the input only takes the minimum and maximum values \cite{BangBangControl}.
 D'Andrea's pitch rate is bang-singular, meaning the control input is always at full positive or negative saturation, except during singular arcs \cite{D'Andrea}.
@@
 	In our model, the inputs were free to vary as continuously as possible between the bounds set in table \ref{Problem Bounds}.
-Despite this, both models arrived at the destination $x=z=5$ following the same time-optimal path and input behavior.
+Despite this, both models arrived at the destination $x=z=5$ following approximately the same time-optimal path and input behavior.
 

### 2017-08-16 Controller.m
changed iterating index to start on step 1 instead of 2

@@ -89,8 +89,6 @@ function [actuators,data] = runControlSystem(sensors,references,parameters,data)
 % Reference trajectory
 ind = data.index;
 if data.index < length(data.trajT)
-    data.index = data.index + 1;
-    
     trajX = data.trajX(ind);
     trajXdot = data.trajXdot(ind);
     trajZ = data.trajZ(ind);
@@ -98,6 +96,7 @@ if data.index < length(data.trajT)
     trajTheta = data.trajTheta(ind);
     trajW = data.trajW(ind);
     trajF = data.trajF(ind);
+    data.index = data.index + 1;
 else
     data.index = data.index+1;
     trajX = data.trajX(end);

### 2017-08-16 Papers/main.tex
Add files via upload

--- 2017-08-15 Papers/DroneInTheWind.tex
@@
 \author{Nico Alba, Isabel Anderson, Emilio Gordon, Michael Gray, Will Reyes}
-\date{July, 2017}
 
@@
 The simulated drone as of the point of writing this paper is equipped with sensors to measure the velocity in the horizontal and vertical axis, the vertical position and the pitch angle.
-The goal is to create a controller that linearizes about a trajectory given by the third-party program OptimTraj.
-The trajectory comes from a cost function that minimizes the time integral of error from a desired position.
+The goal is to create a controller that linearizes about a time optimal trajectory given by the third-party program OptimTraj.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{state}
-x = \begin{bmatrix} x\\ \dot{x} \\ z \\ \dot{z} \\ \theta \end{bmatrix}
+\dot{x} = \begin{bmatrix} \dot{x}\\ \frac{f\sin{\theta}}{m} \\ \dot{z} \\ \frac{f\cos{\theta}}{m} - g \\ \omega \end{bmatrix}
+= \frac{d}{dt}
+\begin{bmatrix} x \\ \dot{x} \\ z \\ \dot{z} \\ \theta 
+\end{bmatrix}
 \end{equation}
@@
 \end{equation}
-Substituting the equilibrium force, $f = mg$, results in the following matrices shown in Equation \ref{A_matrix} and Equation \ref{B_matrix}.
-\begin{equation}
-\label{A_matrix}
-A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && g\cos{\theta} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && -g\sin{\theta} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
-\end{equation}
-
-\begin{equation}
-\label{B_matrix}
-B = \begin{bmatrix} 0 && 0 \\ 0 && \frac{\sin{\theta}}{m} \\ 0 && 0 \\ 0 && \frac{\cos{\theta}}{m} \\ 1 && 0 \end{bmatrix}
-\end{equation}
+There is no need to substitute in equilibrium conditions because we will be linearizing about a trajectory.
 
@@
 OptimTraj \cite{OptimTraj} was used for trajectory planning.
-OptiTraj is a MATLAB library designed by a Cornell PHD student, Matthew P.
+OptimTraj is a MATLAB library designed by a Cornell PHD student, Matthew P.
 Kelly, to solve for continuous-time single-phase trajectory optimization problems.
@@
 
-\clearpage
-
 \subsubsection{Cost Function}
@@
 \end{quote}
+For our purposes, we explicitly used the "Time objective function for boundary points" and the other cost functions were commented out.
+
+\clearpage
 
@@
 \subsubsection{Solution}
-Finally, running the command \lstinline!soln = optimTraj(problem)! is used to solve. Following this, it is possible to unpack the simulation, save the data, and plot out.
+Finally, running the command \lstinline!soln = optimTraj(problem)! is used to solve. Following this, it is possible to unpack the simulation, save the data, and plot it.
 \begin{quote}
@@
 is to keep the grid-spacing of the simulation and optimal trajectory path the same.
-This will be elaborated on a further in Section \ref{Running Simulation}.
+This will be elaborated on further in Section \ref{Running Simulation}.
 
@@
 The controller is designed to use in the loop control with LQR to follow a given trajectory.
-First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ is the only variable.
+First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ and the thrust $f$ are the only variables.
 These symbolic descriptions are then turned into MATLAB functions and saved in the data struct.
@@
 If there is not, the controller will linearize about the last available trajectory point.
-This case does not happen in current simulations because the trajectory is planned for the entire duration of the simulation.
 \begin{quote}
 \begin{lstlisting}
-% Create functions
-if data.index <= length(data.T)
-    data.x_eq = [data.X(data.index);
-                 data.Xdot(data.index);
-                 data.Z(data.index);
-                 data.Zdot(data.index);
-                 data.Theta(data.index)];
-
+% Reference trajectory
+ind = data.index;
+if data.index < length(data.trajT)
+    trajX = data.trajX(ind);
+    trajXdot = data.trajXdot(ind);
+    trajZ = data.trajZ(ind);
+    trajZdot = data.trajZdot(ind);
+    trajTheta = data.trajTheta(ind);
+    trajW = data.trajW(ind);
+    trajF = data.trajF(ind);
     data.index = data.index + 1;
-end
 
@@
 After determining that the simulation is still within the regime in which a trajectory is available, the controller will find the respective trajectory point to linearize about for the current time-step.
-The angle for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
+The angle and thrust for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
 \begin{quote}
 \begin{lstlisting}
-theta = data.x_eq(5,1);
-A = data.funcA(theta);
-B = data.funcB(theta);
+A = data.funcA(trajTheta,trajF);
+B = data.funcB(trajTheta);
+data.K = lqr(A,B,data.Q,data.R);
 
@@
 
-Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.
-Note here that for hover, the thrust \textit{must} augmented by the equilibrium condition, $f = mg$.
-K is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.
+Finally, the input $u = -Kx + n$ is applied in which $K$ is the previously specified gain matrix, $x$ is the difference between the current state and the trajectory state at the current time, and $n$ is the trajectory input at the current time.
+As an example, when the quadroter is meant to be at hover, $n = -mg$.
 
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-To run the simulation, a function named \lstinline!automation.m! was used to set up the problem bounds, plan the optimal trajectory, and analyze the results. Below is shown the script to do so.
+To run the simulation, a function named \lstinline!automation.m! was used to set up the problem bounds, plan the optimal trajectory, and analyze the results. Shown below is the script to do so.
 \begin{quote}
@@
 \newline
-\lstinline!AnalysisOfOptimalTrajectory()!
-plots the simulation against the optimal trajectory calculated by optimTraj.
-\textbf{Solid lines} are to show the optimal trajectory, and \textbf{dashed lines} show the simulated quad-rotor path.
+\lstinline!AnalysisOfOptimalTrajectory()! plots the simulation against the optimal trajectory calculated by optimTraj.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 First the Optimal trajectory was calculated and saved, then the simulation was run and data stored, and finally both results were plotted against each other.
-To reiterate, \textbf{Solid lines} are to show the optimal trajectory, and \textbf{dashed lines} show the simulated quad-rotor path.
+\textbf{Solid lines} show the optimal trajectory, and \textbf{dashed lines} show the simulated quad-rotor path.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage
 \subsection{Simulation Analysis}
+
 \begin{quote}
@@
 \newline
-Reminder, \textbf{Solid lines} show the calculated optimal trajectory. \textbf{Dashed lines} show the simulated quad-rotor path.
-
-\begin{figure}[h!]
-  \centering
-  \begin{minipage}[b]{0.5\textwidth}
-    \includegraphics[width=\textwidth]{State.png}
-    \caption{\label{State Plot} Quadcopter state over time.}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{Inputs.png}
-    \caption{\label{Input Plot} Quadcopter Inputs over time.}
-  \end{minipage}
-\end{figure}
 
@@
 
+Reminder, \textbf{Solid lines} show the calculated optimal trajectory. \textbf{Dashed lines} show the simulated quad-rotor path.
+
+\begin{figure}[h!]
+  \centering
+  \begin{minipage}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{State.png}
+    \caption{\label{State Plot} Quadcopter state over time.}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{Inputs.png}
+    \caption{\label{Input Plot} Quadcopter Inputs over time.}
+  \end{minipage}
+\end{figure}
+
 \begin{figure}[H]
@@
 Though both results are nearly identical, the biggest difference in performance is in that of the inputs. 
-D'Andrea input for thrust is bang-bang, meaning there is a switch discontinuity AND the input only takes the minimum and maximum values \cite{BangBangControl}.
+D'Andrea input for thrust is bang-bang, meaning there is a switch discontinuity and the input only takes the minimum and maximum values \cite{BangBangControl}.
 D'Andrea's pitch rate is bang-singular, meaning the control input is always at full positive or negative saturation, except during singular arcs \cite{D'Andrea}.
@@
 In our model, the inputs were free to vary as continuously as possible between the bounds set in table \ref{Problem Bounds}.
-Despite this, both models arrived at the destination $x=z=5$ following the same time-optimal path and input behavior.
+Despite this, both models arrived at the destination $x=z=5$ following approximately the same time-optimal path and input behavior.
+In order to completely match input behavior, this issue may be resolved through tinkering with OptimTraj.
 
@@
 
-\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 With the completion of a 2D optimized drone path, plans to enhance the simulation are underway.
-Several additions will be added to the current simulation in order to complete this task.
+Two main additions will be added to the current simulation in order to complete this task.
 Those are as follows

### 2017-08-18 AnalysisOfOptimalTrajectory.m
Add files via upload

@@ -7,8 +7,16 @@ uopt = u;
 
 load data
 tsim = processdata.t;
-xsim = [processdata.x; processdata.xdot; processdata.z; processdata.zdot; processdata.theta];
-usim = [controllerdata.actuators.pitchrate; controllerdata.actuators.thrust];
+xsim = [processdata.x; processdata.xdot;
+        processdata.y; processdata.ydot;
+        processdata.z; processdata.zdot; 
+        processdata.theta
+        processdata.phi;
+        processdata.psi];
+usim = [controllerdata.actuators.pitchrate; 
+        controllerdata.actuators.rollrate;
+        controllerdata.actuators.yawrate;
+        controllerdata.actuators.thrust];
 
 clf;
 

### 2017-08-18 Linearization.m

@@ -1,0 +1,31 @@
+clear all clc
+syms x y z xdot ydot zdot  THRUST m g real
+syms theta w phi p psi r real
+m = 1;
+EOMs = [xdot;
+        (THRUST/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi));
+        ydot;
+        (THRUST/m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))
+        zdot;
+        (THRUST/m)*cos(theta)*cos(phi)-9.81;
+        w;
+        p;
+        r];
+    
+
+State = [x; xdot; y; ydot; z; zdot; theta; phi;psi];
+Input = [w;p;r;THRUST];
+
+A = jacobian(EOMs,State)
+B = jacobian(EOMs,Input)
+funcA = matlabFunction(A);
+funcA
+funcB = matlabFunction(B);
+funcB
+A = funcA (9.81,0,0,0);
+B = funcB(0,0,0);
+
+rank(ctrb(A,B))
+
+% A = [0 1 0 0 0 0 0;0 0 0 0 0 0 9.81;0 0 0 1 0 0 0;0 0 0 0 0 0 -9.81;0 0 0 0 0 1 0;0 0 0 0 0 0 0;0 0 0 0 0 0 0]
+% B = [0 0;0 0;0 0;0 0;0 0;0 1;1 0];

### 2017-08-18 analysis.m

@@ -2,9 +2,12 @@ load('data.mat')
 t = processdata.t;
 x = processdata.x;
 xdot = processdata.xdot;
+y = processdata.y;
+ydot = processdata.ydot;
 z = processdata.z;
 zdot = processdata.zdot;
 theta = processdata.theta;
+phi = processdata
 f = controllerdata.actuators.thrust;
 w = controllerdata.actuators.pitchrate;
 %plot(t,x,t,xdot,t,z,t,zdot,t,theta)

### 2017-08-18 automate.m

@@ -1,15 +1,18 @@
 % Constants to be applied
 clear; 
-xFinal = 5;
-zFinal = 5;
+xFinal = 3;
+yFinal = 0;
+zFinal = 3;
 timeDensity = 400;
-runTime = 2;
+runTime = 7;
 
 
 gravity = 9.81;
 mass = 1;
 
 maxPitchRate = 10;
+maxRollRate = 10;
+maxYawRate = 10;
 maxThrust = 20;
 minThrust = 1;
 

### 2017-08-18 planOptimalTrajectory.m

@@ -4,6 +4,8 @@ load('runOptions')
 
 xInitial = 0;
 zInitial = 0;
+yInitial = 0;
+
 m = mass;
 g = gravity;
 
@@ -13,17 +15,23 @@ g = gravity;
 
 
 % Put symbolic EOMs in convenient form
-syms x xdot z zdot theta thrust w real
+syms x xdot y ydot z zdot theta phi psi thrust w p r real
 f = simplify([xdot; 
-              (thrust/m)*sin(theta); 
+              (thrust/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi)); 
+              ydot;
+              (sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))
               zdot; 
-              (thrust/m)*cos(theta) - g; 
-              w]);
+              (thrust/m)*cos(theta)*cos(phi) - g; 
+              w;
+              p;
+              r]);
+              
 % Convert EOMs from symbolic to numeric
-numf = matlabFunction(f,'vars',[x xdot z zdot theta w thrust]);
+numf = matlabFunction(f,'vars',[x xdot y ydot z zdot theta w phi p psi r thrust]);
 
-problem.func.dynamics = @(t,x,u)( numf(x(1,:), x(2,:), x(3,:), x(4,:), x(5,:),... 
-                                       u(1,:), u(2,:)) );
+problem.func.dynamics = @(t,x,u)( numf(x(1,:), x(2,:), x(3,:), x(4,:), x(5,:),...
+                                       x(6,:), x(7,:), x(8,:), x(9,:),...
+                                       u(1,:), u(2,:), u(3,:), u(4,:) ));
                                    
                                    
                                    
@@ -54,14 +62,18 @@ problem.bounds.initialTime.upp = 0;
 problem.bounds.finalTime.low = 0;
 problem.bounds.finalTime.upp = runTime;
 
-problem.bounds.initialState.low = [xInitial; 0; zInitial; 0; 0];
-problem.bounds.initialState.upp = [xInitial; 0; zInitial; 0; 0];
-problem.bounds.finalState.low = [xFinal; 0; zFinal; 0; 0];
-problem.bounds.finalState.upp = [xFinal; 0; zFinal; 0; 0];
[…]

### 2017-08-22 AnalysisOfOptimalTrajectory.m
Add files via upload

@@ -28,8 +28,8 @@ for i = 1:6
     plot(tsim,xsim(i,:))
     hold on
 end
-title('Simulation')
-legend('x','xdot','y','ydot','z','zdot')
+title('Simulation Pos & Vel')
+legend('x','xdot','y','ydot','z','zdot','location','northwest')
 grid on
 xlim([topt(1) topt(end)]);
 subplot(2,1,2)
@@ -37,8 +37,9 @@ for i = 1:6
     plot(topt,xopt(i,:))
     hold on
 end
-title('OptimTraj')
-legend('x','xdot','y','ydot','z','zdot')
+title('OptimTraj Pos & Vel')
+xlim([topt(1) topt(end)]);
+legend('x','xdot','y','ydot','z','zdot','location','northwest')
 grid on
 
 figure(2)
@@ -47,8 +48,8 @@ for i = 7:9
     plot(tsim,xsim(i,:))
     hold on
 end
-title('Simulation')
-legend('\theta','\phi','\psi')
+title('Simulation Angles')
+legend('\theta','\phi','\psi','location','southwest')
 xlim([topt(1) topt(end)]);
 grid on
 subplot(2,1,2)
@@ -56,8 +57,10 @@ for i = 7:9
     plot(topt,xopt(i,:))
     hold on
 end
-title('OptimTraj')
-legend('\theta','\phi','\psi')
+title('OptimTraj Angles')
+
+xlim([topt(1) topt(end)]);
+legend('\theta','\phi','\psi','location','southwest')
 grid on
 
 
@@ -67,10 +70,10 @@ for i = 1:4
     plot(tsim,usim(i,:))
     hold on
 end
-title('Simulation')
+title('Simulation Input')
 xlim([topt(1) topt(end)]);
 grid on
-hl = legend('$\dot{\theta}$','$\dot{\phi}$','$\dot{\psi}$');
+hl = legend('$\dot{\theta}$','$\dot{\phi}$','$\dot{\psi}$','location','northwest');
 set(hl, 'Interpreter', 'latex');
 % xlabel('$\dot{T}$'),ylabel('$\dot{y}');
 
@@ -80,9 +83,11 @@ for i = 1:4
     plot(topt,uopt(i,:))
     hold on
 end
-title('OptimTraj')
+title('OptimTraj Input')
+
+xlim([topt(1) topt(end)]);
 grid on
[…]

### 2017-08-22 Controller.m

@@ -113,34 +113,34 @@ function [actuators,data] = runControlSystem(sensors,references,parameters,data)
 % Reference trajectory
 ind = data.index;
 if data.index < length(data.trajT)
-    Time_diff = abs(data.trajT(data.index)-sensors.t)
+%     Time_diff = abs(data.trajT(data.index)-sensors.t)
     data.index = data.index + 1;    
-    trajX = data.trajX(ind);
-    trajXdot = data.trajXdot(ind);
-    trajY = data.trajY(ind);
-    trajYdot = data.trajYdot(ind);
-    trajZ = data.trajZ(ind);
-    trajZdot = data.trajZdot(ind);
-    trajTheta = data.trajTheta(ind);
-    trajPhi = data.trajPhi(ind);
-    trajPsi = data.trajPsi(ind);
+%     trajX = data.trajX(ind);
+%     trajXdot = data.trajXdot(ind);
+%     trajY = data.trajY(ind);
+%     trajYdot = data.trajYdot(ind);
+%     trajZ = data.trajZ(ind);
+%     trajZdot = data.trajZdot(ind);
+%     trajTheta = data.trajTheta(ind);
+%     trajPhi = data.trajPhi(ind);
+%     trajPsi = data.trajPsi(ind);
     
     trajW = data.trajW(ind);
     trajP = data.trajP(ind);
     trajR = data.trajR(ind);
     trajF = data.trajF(ind);
 else
-    
-    trajX = data.trajX(end);
-    trajXdot = data.trajXdot(end);
-    trajY = data.trajY(end);
-    trajYdot = data.trajYdot(end);
-    trajZ = data.trajZ(end);
-    trajZdot = data.trajZdot(end);
-    trajTheta = data.trajTheta(end);
-    trajPhi = data.trajPhi(end);
-    trajPsi = data.trajPsi(end);
-    
+%     
+%     trajX = data.trajX(end);
+%     trajXdot = data.trajXdot(end);
+%     trajY = data.trajY(end);
+%     trajYdot = data.trajYdot(end);
+%     trajZ = data.trajZ(end);
+%     trajZdot = data.trajZdot(end);
+%     trajTheta = data.trajTheta(end);
+%     trajPhi = data.trajPhi(end);
+%     trajPsi = data.trajPsi(end);
+%     
     
     trajW = 0;
     trajP = 0;
[…]

### 2017-08-22 DesignProblemSummer2017.m

@@ -326,10 +326,10 @@ r = U(3,1);
 f = U(4,1);
 % compute rates of change
 d_x = xdot;
-d_xdot = (f/process.m)*sin(theta)*cos(phi) + 0; %MODIFICATION: Wind
+d_xdot = (f/process.m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi)) + 0; %MODIFICATION: Wind
 
 d_y = ydot;
-d_ydot = (-f/process.m)*sin(phi);
+d_ydot = (f/process.m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi));
 
 d_z = zdot;
 d_zdot = (f/process.m)*cos(theta)*cos(phi)-process.g;

### 2017-08-22 automate.m

@@ -1,8 +1,8 @@
 % Constants to be applied
 clear; 
-xFinal = 5;
-yFinal = 5;
-zFinal = 5;
+xFinal = -3;
+yFinal = 1;
+zFinal = 2;
 timeDensity = 400;
 runTime = 4;
 

### 2017-08-22 Linearization.m
removed Linearization

@@ -1,31 +1,0 @@
-clear all clc
-syms x y z xdot ydot zdot  THRUST m g real
-syms theta w phi p psi r real
-m = 1;
-EOMs = [xdot;
-        (THRUST/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi));
-        ydot;
-        (THRUST/m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))
-        zdot;
-        (THRUST/m)*cos(theta)*cos(phi)-9.81;
-        w;
-        p;
-        r];
-    
-
-State = [x; xdot; y; ydot; z; zdot; theta; phi;psi];
-Input = [w;p;r;THRUST];
-
-A = jacobian(EOMs,State)
-B = jacobian(EOMs,Input)
-funcA = matlabFunction(A);
-funcA
-funcB = matlabFunction(B);
-funcB
-A = funcA (9.81,0,0,0);
-B = funcB(0,0,0);
-
-rank(ctrb(A,B))
-
-% A = [0 1 0 0 0 0 0;0 0 0 0 0 0 9.81;0 0 0 1 0 0 0;0 0 0 0 0 0 -9.81;0 0 0 0 0 1 0;0 0 0 0 0 0 0;0 0 0 0 0 0 0]
-% B = [0 0;0 0;0 0;0 0;0 0;0 1;1 0];

### 2017-08-22 Controller.m
Add files via upload

@@ -85,7 +85,6 @@ data.trajW = u(1,:);
 data.trajP = u(2,:);
 data.trajR = u(3,:);
 data.trajF = u(4,:);
-data.index = 1;
 
 load('runOPtions.mat')
 data.minThrust = minThrust;
@@ -95,7 +94,7 @@ data.maxRollRate = maxRollRate;
 data.maxYawRate = maxYawRate;
 
 % Analysis variables
-data.vel_error = .05;  % Required velocity from rest (for both x and z)
+data.vel_error = .5;  % Required velocity from rest (for both x and z)
 data.pos_error = .05;  % Required distance from final position (for both x and z)
 data.endBool = 0;      % Used to only display the end time once
 
@@ -114,32 +113,34 @@ function [actuators,data] = runControlSystem(sensors,references,parameters,data)
 ind = data.index;
 if data.index < length(data.trajT)
 %     Time_diff = abs(data.trajT(data.index)-sensors.t)
+    
     data.index = data.index + 1;    
-%     trajX = data.trajX(ind);
-%     trajXdot = data.trajXdot(ind);
-%     trajY = data.trajY(ind);
-%     trajYdot = data.trajYdot(ind);
-%     trajZ = data.trajZ(ind);
-%     trajZdot = data.trajZdot(ind);
-%     trajTheta = data.trajTheta(ind);
-%     trajPhi = data.trajPhi(ind);
-%     trajPsi = data.trajPsi(ind);
+    
+    trajX = data.trajX(ind);
+    trajXdot = data.trajXdot(ind);
+    trajY = data.trajY(ind);
+    trajYdot = data.trajYdot(ind);
+    trajZ = data.trajZ(ind);
+    trajZdot = data.trajZdot(ind);
+    trajTheta = data.trajTheta(ind);
+    trajPhi = data.trajPhi(ind);
+    trajPsi = data.trajPsi(ind);
     
     trajW = data.trajW(ind);
     trajP = data.trajP(ind);
     trajR = data.trajR(ind);
     trajF = data.trajF(ind);
 else
-%     
-%     trajX = data.trajX(end);
-%     trajXdot = data.trajXdot(end);
-%     trajY = data.trajY(end);
-%     trajYdot = data.trajYdot(end);
-%     trajZ = data.trajZ(end);
[…]

### 2017-08-22 DesignProblemSummer2017.m

@@ -216,7 +216,7 @@ end
 
 function u = GetInput(process,actuators)
 % Copy input from actuators
-u = [actuators.pitchrate; actuators.rollrate; actuators.yawrate; actuators.thrust];
+% u = [actuators.pitchrate; actuators.rollrate; actuators.yawrate; actuators.thrust];
 
 % Initialize inputs to zero
 u = zeros(4,1);
@@ -325,14 +325,24 @@ p = U(2,1);
 r = U(3,1);
 f = U(4,1);
 % compute rates of change
+
+dimensions = [651 651 188];
+A = (dimensions(1)/1000)^2; 
+c_d = 0.05;
+rho = 1.225; %kg/m^3
+
+vel = [xdot;ydot;zdot];
+Fd = (-.5*c_d*rho*A*norm(vel)*vel);
+
+
 d_x = xdot;
-d_xdot = (f/process.m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi)) + 0; %MODIFICATION: Wind
+d_xdot = (f/process.m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi)) +Fd(1)/process.m; %Fd(1)/process.m; %MODIFICATION: Wind
 
 d_y = ydot;
-d_ydot = (f/process.m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi));
+d_ydot = (f/process.m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))+Fd(2)/process.m;
 
 d_z = zdot;
-d_zdot = (f/process.m)*cos(theta)*cos(phi)-process.g;
+d_zdot = (f/process.m)*cos(theta)*cos(phi)-process.g+Fd(3)/process.m;
 
 d_theta = w;
 d_phi = p;
@@ -417,7 +427,7 @@ if (isempty(fig))
     box on;
     
 %     view([0 0])  % XZ Plane
-%     view([0,90]) % XY Plane
+    view([0,90]) % XY Plane
 %     view([90,0]) %YZ Plane
      view([45,20])
       % Draws room axis: 
@@ -448,7 +458,7 @@ else
     
       % Draws robot and then robot axis
       fig.robot = DrawMesh(fig.robot,process.pRobot_in0,process.fRobot);
-      fig.robotframe = DrawFrame(fig.robotframe,process.pRobotFrame_in0);
[…]

### 2017-08-22 automate.m

@@ -1,10 +1,16 @@
 % Constants to be applied
 clear; 
-xFinal = -3;
-yFinal = 1;
-zFinal = 2;
+xFinal = 5;
+yFinal = 0;
+zFinal = 5;
 timeDensity = 400;
 runTime = 4;
+
+% windX = 1;
+% windY = 1;
+% windZ = 1;
+% 
+% wind = [windx;windY;windZ];     % m/s
 
 
 gravity = 9.81;

### 2017-08-22 planOptimalTrajectory.m

@@ -9,19 +9,42 @@ yInitial = 0;
 m = mass;
 g = gravity;
 
+dimensions = [651 651 188];
+A = (dimensions(1)/1000)^2; 
+c_d = 0.05;
+rho = 1.225; %kg/m^3
+
+[x_n,y_n] = meshgrid(-5:0.1:5,-5:0.1:5);
+u_n = cos(x_n).*y_n;
+v_n = sin(x_n).*y_n;
+figure
+quiver(x_n,y_n,u_n,v_n)
+
+
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 %                     Set up function handles                             %
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 
 
+
 % Put symbolic EOMs in convenient form
 syms x xdot y ydot z zdot theta phi psi thrust w p r real
+
+vel = [xdot;ydot;zdot];
+pos = [x;y;z];
+
+wind_u = cos(x)*y;
+wind_v = sin(x)*y;
+
+Fd = (-.5*c_d*rho*A*norm(vel)^2 *vel)/norm(vel);
+% Fd = [0;0;0]
+
 f = simplify([xdot; 
-              (thrust/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi)); 
+              (thrust/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi))+Fd(1)/m+wind_u; 
               ydot;
-              (thrust/m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))
+              (thrust/m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))+Fd(2)/m+wind_v;
               zdot; 
-              (thrust/m)*cos(theta)*cos(phi) - g; 
+              (thrust/m)*cos(theta)*cos(phi)-g+Fd(3)/m;
               w;
               p;
               r]);

### 2017-08-22 analysis.m
Delete analysis.m

@@ -1,20 +1,0 @@
-load('data.mat')
-t = processdata.t;
-x = processdata.x;
-xdot = processdata.xdot;
-y = processdata.y;
-ydot = processdata.ydot;
-z = processdata.z;
-zdot = processdata.zdot;
-theta = processdata.theta;
-phi = processdata
-f = controllerdata.actuators.thrust;
-w = controllerdata.actuators.pitchrate;
-%plot(t,x,t,xdot,t,z,t,zdot,t,theta)
-plot(t,f)
-%legend('x','xdot','z','zdot','theta')
-xlabel('Time, t')
-%ylabel('m, m/s, rad')
-ylabel('Thrust, N')
-title('5 Second, time optimal')
-grid on

### 2017-08-23 AnalysisOfOptimalTrajectory.m
changed input to 4 forces and one moment

@@ -73,7 +73,7 @@ end
 title('Simulation Input')
 xlim([topt(1) topt(end)]);
 grid on
-hl = legend('$\dot{\theta}$','$\dot{\phi}$','$\dot{\psi}$','location','northwest');
+hl = legend('$\dot{\theta}$','$\dot{\phi}$','$\dot{\psi}$','thrust','location','northwest');
 set(hl, 'Interpreter', 'latex');
 % xlabel('$\dot{T}$'),ylabel('$\dot{y}');
 
@@ -87,7 +87,7 @@ title('OptimTraj Input')
 
 xlim([topt(1) topt(end)]);
 grid on
-hl = legend('$\dot{\theta}$','$\dot{\phi}$','$\dot{\psi}$','location','northwest');
+hl = legend('$\dot{\theta}$','$\dot{\phi}$','$\dot{\psi}$','thrust','location','northwest');
 set(hl, 'Interpreter', 'latex');
 
 % 

### 2017-08-23 automate.m

@@ -1,24 +1,27 @@
 % Constants to be applied
 clear; 
-xFinal = -3;
-yFinal = 1;
-zFinal = 2;
+xFinal = 5;
+yFinal = 0;
+zFinal = 5;
 timeDensity = 400;
 runTime = 4;
 
-
 gravity = 9.81;
 mass = 1;
+Ix = 1;
+Iy = 1;
+Iz = .5;
 
 maxPitchRate = 10;
-maxRollRate = 10;
-maxYawRate = 10;
-maxThrust = 20;
-minThrust = 1;
+% maxRollRate = 10;
+% maxYawRate = 10;
+maxThrust = 20/4;
+minThrust = 1/4;
 
 save('runOptions.mat');
 
-%Run the three scripts
+%Run the four scripts
+eoms()
 planOptimalTrajectory()
 DesignProblemSummer2017('Controller','datafile','data.mat')
 AnalysisOfOptimalTrajectory()

### 2017-08-23 planOptimalTrajectory.m

@@ -9,29 +9,58 @@ yInitial = 0;
 m = mass;
 g = gravity;
 
+dimensions = [651 651 188];
+A = (dimensions(1)/1000)^2; 
+c_d = 0.05;
+rho = 1.225; %kg/m^3
+
+% [x_n,y_n] = meshgrid(-5:0.1:5,-5:0.1:5);
+% u_n = cos(x_n).*y_n;
+% v_n = sin(x_n).*y_n;
+% figure
+% quiver(x_n,y_n,u_n,v_n)
+
+
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 %                     Set up function handles                             %
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 
 
+
 % Put symbolic EOMs in convenient form
-syms x xdot y ydot z zdot theta phi psi thrust w p r real
+syms x xdot y ydot z zdot phi theta psi phidot thetadot psidot ...
+    f1 f2 f3 f4 r real
+
+vel = [xdot;ydot;zdot];
+pos = [x;y;z];
+
+% wind_u = cos(x)*y;
+% wind_v = sin(x)*y;
+
+Fd = (-.5*c_d*rho*A*norm(vel)^2 *vel)/norm(vel);
+% Fd = [0;0;0]
+
 f = simplify([xdot; 
-              (thrust/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi)); 
+              ((f1+f2+f3+f4)/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi))+Fd(1)/m; %+wind_u; 
               ydot;
-              (thrust/m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))
+              ((f1+f2+f3+f4)/m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))+Fd(2)/m; %+wind_v;
               zdot; 
-              (thrust/m)*cos(theta)*cos(phi) - g; 
-              w;
-              p;
-              r]);
+              ((f1+f2+f3+f4)/m)*cos(theta)*cos(phi)-g+Fd(3)/m;
+              phidot;
+              nddot(1)
+              thetadot;
[…]

### 2017-08-24 automate.m
4 control forces, one control moment not implemented in DesignProblemSummer2017 yet

@@ -6,25 +6,22 @@ zFinal = 5;
 timeDensity = 400;
 runTime = 4;
 
-% windX = 1;
-% windY = 1;
-% windZ = 1;
-% 
-% wind = [windx;windY;windZ];     % m/s
-
-
 gravity = 9.81;
 mass = 1;
+Ix = 1;
+Iy = 1;
+Iz = .5;
 
 maxPitchRate = 10;
-maxRollRate = 10;
-maxYawRate = 10;
-maxThrust = 20;
-minThrust = 1;
+% maxRollRate = 10;
+% maxYawRate = 10;
+maxThrust = 20/4;
+minThrust = 1/4;
 
 save('runOptions.mat');
 
-%Run the three scripts
+%Run the four scripts
+eoms()
 planOptimalTrajectory()
 DesignProblemSummer2017('Controller','datafile','data.mat')
 AnalysisOfOptimalTrajectory()

### 2017-08-24 eoms.m

@@ -1,0 +1,27 @@
+load('runOptions.mat')
+syms phi theta psi phidot thetadot psidot f1 f2 f3 f4 r
+M = [Ix 0 -Ix*sin(theta); ...
+    0 Iy*cos(phi)^2+Iz*sin(phi)^2 (Iy-Iz)*cos(phi)*sin(phi)*cos(theta); ...
+    -Ix*sin(theta) (Iy-Iz)*cos(phi)*sin(phi)*cos(theta)...
+    Ix*sin(theta)^2+Iy*sin(phi)^2*cos(theta)^2+Iz*cos(phi)^2*cos(theta)^2];
+c11 = 0;
+c12 = (Iy-Iz)*(thetadot*cos(phi)*sin(phi)+psi*sin(phi)^2*cos(theta)) ...
+    + (Iz-Iy)*psi*cos(phi)^2*cos(theta) - Ix*psi*cos(theta);
+c13 = (Iz-Iy)*psidot*cos(phi)*sin(phi)*cos(theta)^2;
+c21 = (Iz-Iy)*(thetadot*cos(phi)*sin(phi)+psi*sin(phi)^2*cos(theta)) ...
+    + (Iy-Iz)*psi*cos(phi)^2*cos(theta) + Ix*psi*cos(theta);
+c22 = (Iz-Iy)*phidot*cos(phi)*sin(phi);
+c23 = -Ix*psidot*sin(theta)*cos(theta) + Iy*psidot*sin(phi)^2*cos(theta)*sin(theta) ...
+    + Iz*psidot*cos(phi)^2*sin(theta)*cos(theta);
+c31 = (Iy-Iz)*psi*cos(theta)^2*sin(phi)*cos(phi) - Ix*thetadot*cos(theta);
+c32 = (Iz-Iy)*(thetadot*cos(phi)*sin(phi)*sin(theta) + phidot*sin(phi)^2*cos(theta)) ...
+    + (Iy-Iz)*phidot*cos(phi)^2*cos(theta) + Ix*psidot*sin(theta)*cos(theta) ...
+    - Iy*psidot*sin(phi)^2*cos(theta)*sin(theta) - Iz*psidot*cos(phi)^2*sin(theta)*cos(theta);
+c33 = (Iy-Iz)*psidot*cos(theta)^2*sin(phi)*cos(phi) - Iy*thetadot*sin(phi)^2*cos(theta)*sin(theta) ...
[…]

### 2017-08-24 planOptimalTrajectory.m

@@ -14,11 +14,11 @@ A = (dimensions(1)/1000)^2;
 c_d = 0.05;
 rho = 1.225; %kg/m^3
 
-[x_n,y_n] = meshgrid(-5:0.1:5,-5:0.1:5);
-u_n = cos(x_n).*y_n;
-v_n = sin(x_n).*y_n;
-figure
-quiver(x_n,y_n,u_n,v_n)
+% [x_n,y_n] = meshgrid(-5:0.1:5,-5:0.1:5);
+% u_n = cos(x_n).*y_n;
+% v_n = sin(x_n).*y_n;
+% figure
+% quiver(x_n,y_n,u_n,v_n)
 
 
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
@@ -28,33 +28,39 @@ quiver(x_n,y_n,u_n,v_n)
 
 
 % Put symbolic EOMs in convenient form
-syms x xdot y ydot z zdot theta phi psi thrust w p r real
+syms x xdot y ydot z zdot phi theta psi phidot thetadot psidot ...
+    f1 f2 f3 f4 r real
 
 vel = [xdot;ydot;zdot];
 pos = [x;y;z];
 
-wind_u = cos(x)*y;
-wind_v = sin(x)*y;
+% wind_u = cos(x)*y;
+% wind_v = sin(x)*y;
 
 Fd = (-.5*c_d*rho*A*norm(vel)^2 *vel)/norm(vel);
 % Fd = [0;0;0]
 
 f = simplify([xdot; 
-              (thrust/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi))+Fd(1)/m+wind_u; 
+              ((f1+f2+f3+f4)/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi))+Fd(1)/m; %+wind_u; 
               ydot;
-              (thrust/m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))+Fd(2)/m+wind_v;
+              ((f1+f2+f3+f4)/m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))+Fd(2)/m; %+wind_v;
               zdot; 
-              (thrust/m)*cos(theta)*cos(phi)-g+Fd(3)/m;
-              w;
-              p;
-              r]);
[…]

### 2017-08-24 Controller.m
Simulation now runs; however the controller is not updated to work with the new EOMs.  For some reason, the simulation does not display the error message that something is wrong with the controller.  Effort has been made to increase the modularity of the process as a whole when changing the physics.  Namely, the file eoms.m is used for creating a symbolic description of the equations of motion that can then be passed into other scripts and used.  Currently the only script that uses it is planOptimalTrajectory.  A divide by zero error hampered it being implented in DesignProblemSummer2017 for u

@@ -7,7 +7,9 @@ close all
 %       .xdot       (x velocity)
 %       .z          (z position)
 %       .zdot       (z velocity)
-%       .theta      (pitch angle)
+%       .phi        (pitch angle)
+%       .theta      (roll angle)
+%       .psi        (yaw angle)
 %
 %   references
 %       
@@ -23,8 +25,11 @@ close all
 %       .whatever       (yours to define - put whatever you want into "data")
 %
 %   actuators
-%       .pitchrate      (pitch angular rate)
-%       .thrust         (net thrust)
+%       .f1             (Thrust of first rotor)
+%       .f2             (Thrust of second rotor)
+%       .f3             (Thrust of third rotor)
+%       .f4             (Thrust of fourth rotor)
+%       .r              (Yaw Moment)
 
 % Do not modify this function.
 func.init = @initControlSystem;

### 2017-08-24 DesignProblemSummer2017.m

@@ -75,6 +75,7 @@ end
 function [process,controller] = SetupSimulation(process)
 
 load('runOptions')
+
 % DEFINE CONSTANTS
 
 % Constants related to simulation.
@@ -85,7 +86,7 @@ process.tStop = runTime; % MODIFICATION: Runtime
 % - Time step.
 process.tStep = 1/timeDensity; % MODIFICATION: Timestep
 % - Names of things to log in datafile, if desired
-process.processdatatolog = {'t','x','xdot','y','ydot','z','zdot','theta','phi','psi'};
+process.processdatatolog = {'t','x','xdot','y','ydot','z','zdot','theta','thetadot','phi','phidot','psi','psidot'};
 
 % Constants related to physical properties.
 % - Acceleration of gravity.
@@ -96,10 +97,6 @@ process.m = mass;
 process.maxthrust = maxThrust;
 % - Minimum thrust
 process.minthrust = minThrust;
-% - Maximum pitch rate
-process.maxpitchrate = maxPitchRate;
-% - Maximum roll rate
-process.maxrollrate = maxRollRate;
 % - Maximum yaw rate
 process.maxyawrate = maxYawRate;
 
@@ -129,12 +126,15 @@ process.ydot = 0;
 % z, zdot - position and velocity
 process.z = 0;
 process.zdot = 0;
-% theta - angle
-process.theta = 0;
-% phi - angle
+% phi - angle and angular velocity
 process.phi = 0;
-% psi - angle
+process.phidot = 0;
+% theta - angle and angular velocity
+process.theta = 0;
+process.thetadot = 0;
+% psi - angle and angular velocity
 process.psi = 0;
+process.psidot = 0;
 
 % DEFINE CONTROLLER
 
@@ -144,7 +144,7 @@ controller = eval(process.controller);
 controller.name = process.controller;
 % Parameters
 % - define a list of constants that will be passed to the controller
-names = {'tStep','g','m','maxthrust','maxpitchrate','maxrollrate','maxyawrate'};
[…]

### 2017-08-24 automate.m

@@ -11,17 +11,18 @@ mass = 1;
 Ix = 1;
 Iy = 1;
 Iz = .5;
+dim_1 = .651;
+dim_2 = .651;
+dim_3 = .188;
 
-maxPitchRate = 10;
-% maxRollRate = 10;
-% maxYawRate = 10;
 maxThrust = 20/4;
 minThrust = 1/4;
+maxYawRate = 10;
 
 save('runOptions.mat');
 
 %Run the four scripts
 eoms()
 planOptimalTrajectory()
-DesignProblemSummer2017('Controller','datafile','data.mat')
-AnalysisOfOptimalTrajectory()
+% DesignProblemSummer2017('Controller','datafile','data.mat')
+% AnalysisOfOptimalTrajectory()

### 2017-08-24 eoms.m

@@ -1,5 +1,5 @@
 load('runOptions.mat')
-syms phi theta psi phidot thetadot psidot f1 f2 f3 f4 r
+syms x xdot y ydot z zdot phi theta psi phidot thetadot psidot f1 f2 f3 f4 r real
 M = [Ix 0 -Ix*sin(theta); ...
     0 Iy*cos(phi)^2+Iz*sin(phi)^2 (Iy-Iz)*cos(phi)*sin(phi)*cos(theta); ...
     -Ix*sin(theta) (Iy-Iz)*cos(phi)*sin(phi)*cos(theta)...
@@ -21,7 +21,38 @@ c33 = (Iy-Iz)*psidot*cos(theta)^2*sin(phi)*cos(phi) - Iy*thetadot*sin(phi)^2*cos
     - Iz*thetadot*cos(phi)^2*cos(theta)*sin(theta) + Ix*thetadot*cos(theta)*sin(theta);
 C = [c11 c12 c13; c21 c22 c23; c31 c32 c33];
 
-T = [(f3-f1)*.651; (f4-f2)*.651; r];
+
+T = [(f3-f1)*dim_1; (f4-f2)*dim_2; r];
 
 nddot = inv(M)*(T-C*[phidot; thetadot; psidot]);
-save('runOptions.mat','nddot','-append');
+
+
+pos = [x;y;z];
+% [x_n,y_n] = meshgrid(-5:0.1:5,-5:0.1:5);
+% u_n = cos(x_n).*y_n;
+% v_n = sin(x_n).*y_n;
+% figure
+% quiver(x_n,y_n,u_n,v_n)
+% wind_u = cos(x)*y;
+% wind_v = sin(x)*y;
+
+vel = [xdot;ydot;zdot];
+A = dim_1*dim_2;
+c_d = 0.05;
+rho = 1.225;
+Fd = (-.5*c_d*rho*A*norm(vel)^2 *vel)/norm(vel);
+
+equationsOfMotion = [xdot; 
+                    ((f1+f2+f3+f4)/mass)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi))+Fd(1)/mass;
+                    ydot;
+                    ((f1+f2+f3+f4)/mass)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))+Fd(2)/mass;
+                    zdot; 
[…]

### 2017-08-24 planOptimalTrajectory.m

@@ -6,55 +6,16 @@ xInitial = 0;
 zInitial = 0;
 yInitial = 0;
 
-m = mass;
-g = gravity;
-
-dimensions = [651 651 188];
-A = (dimensions(1)/1000)^2; 
-c_d = 0.05;
-rho = 1.225; %kg/m^3
-
-% [x_n,y_n] = meshgrid(-5:0.1:5,-5:0.1:5);
-% u_n = cos(x_n).*y_n;
-% v_n = sin(x_n).*y_n;
-% figure
-% quiver(x_n,y_n,u_n,v_n)
-
-
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
 %                     Set up function handles                             %
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
-
-
 
 % Put symbolic EOMs in convenient form
 syms x xdot y ydot z zdot phi theta psi phidot thetadot psidot ...
     f1 f2 f3 f4 r real
 
-vel = [xdot;ydot;zdot];
-pos = [x;y;z];
-
-% wind_u = cos(x)*y;
-% wind_v = sin(x)*y;
-
-Fd = (-.5*c_d*rho*A*norm(vel)^2 *vel)/norm(vel);
-% Fd = [0;0;0]
-
-f = simplify([xdot; 
-              ((f1+f2+f3+f4)/m)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi))+Fd(1)/m; %+wind_u; 
-              ydot;
-              ((f1+f2+f3+f4)/m)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))+Fd(2)/m; %+wind_v;
-              zdot; 
-              ((f1+f2+f3+f4)/m)*cos(theta)*cos(phi)-g+Fd(3)/m;
-              phidot;
-              nddot(1)
-              thetadot;
-              nddot(2)
-              psidot;
-              nddot(3)]);
-              
 % Convert EOMs from symbolic to numeric
-numf = matlabFunction(f,'vars',[x xdot y ydot z zdot phi phidot theta...
+numf = matlabFunction(simplify(equationsOfMotion),'vars',[x xdot y ydot z zdot phi phidot theta...
[…]

### 2017-08-26 AnalysisOfOptimalTrajectory.m
Completed new model of quad, drag had to be removed temporarily

@@ -11,13 +11,14 @@ tsim = processdata.t;
 xsim = [processdata.x; processdata.xdot;
         processdata.y; processdata.ydot;
         processdata.z; processdata.zdot; 
-        processdata.theta
-        processdata.phi;
-        processdata.psi];
-usim = [controllerdata.actuators.pitchrate; 
-        controllerdata.actuators.rollrate;
-        controllerdata.actuators.yawrate;
-        controllerdata.actuators.thrust];
+        processdata.phi; processdata.phidot;
+        processdata.theta; processdata.thetadot
+        processdata.psi; processdata.psidot];
+usim = [controllerdata.actuators.f1; 
+        controllerdata.actuators.f2;
+        controllerdata.actuators.f3;
+        controllerdata.actuators.f4
+        controllerdata.actuators.r];
 
 clf;
 
@@ -29,7 +30,8 @@ for i = 1:6
     hold on
 end
 title('Simulation Pos & Vel')
-legend('x','xdot','y','ydot','z','zdot','location','northwest')
+hl = legend('x','$\dot{x}$','y','$\dot{y}$','z','$\dot{z}$','location','northwest');
+set(hl, 'Interpreter', 'latex');
 grid on
 xlim([topt(1) topt(end)]);
 subplot(2,1,2)
@@ -39,47 +41,50 @@ for i = 1:6
 end
 title('OptimTraj Pos & Vel')
 xlim([topt(1) topt(end)]);
-legend('x','xdot','y','ydot','z','zdot','location','northwest')
+hl = legend('x','$\dot{x}$','y','$\dot{y}$','z','$\dot{z}$','location','northwest');
+set(hl, 'Interpreter', 'latex');
 grid on
 
 figure(2)
 subplot(2,1,1)
-for i = 7:9
+for i = 7:12
     plot(tsim,xsim(i,:))
     hold on
 end
 title('Simulation Angles')
-legend('\theta','\phi','\psi','location','southwest')
+hl = legend('$\phi$','$\dot{\phi}$','$\theta$','$\dot{\theta}$','$\psi$','$\dot{\psi}$','location','southwest');
+set(hl, 'Interpreter', 'latex');
 xlim([topt(1) topt(end)]);
 grid on
 subplot(2,1,2)
-for i = 7:9
+for i = 7:12
     plot(topt,xopt(i,:))
[…]

### 2017-08-26 Controller.m

@@ -39,39 +39,21 @@ end
 
 function [actuators,data] = initControlSystem(sensors,references,parameters,data)
 clc;
-% Current angle of the quad and current thrust (this will be passed in from the run function)
-syms Psi theta phi f real
-
+load('runOptions')
+syms x xdot y ydot z zdot phi phidot theta thetadot psi psidot f1 f2 f3 f4 r real
 % Symbolic description of A matrix
-A = [
-0, 1, 0, 0, 0, 0,               0,                                                          0,                                0;
-0, 0, 0, 0, 0, 0, f*cos(phi)*cos(Psi)*cos(theta),  f*(cos(phi)*sin(Psi)-cos(Psi)*sin(phi)*sin(theta)), f*(cos(Psi)*sin(phi)-cos(phi)*sin(Psi)*sin(theta));
-0, 0, 0, 1, 0, 0,               0,                                                          0,                                0;
-0, 0, 0, 0, 0, 0, f*cos(phi)*cos(theta)*sin(Psi), -f*(cos(phi)*cos(Psi) + sin(phi)*sin(Psi)*sin(theta)), f*(sin(phi)*sin(Psi) + cos(phi)*cos(Psi)*sin(theta));
-0, 0, 0, 0, 0, 1,               0,                                                          0,                                0;
-0, 0, 0, 0, 0, 0,      -f*cos(phi)*sin(theta),                                -f*cos(theta)*sin(phi),                         0;
-0, 0, 0, 0, 0, 0,               0,                                                          0,                                0;
-0, 0, 0, 0, 0, 0,               0,                                                          0,                                0;
-0, 0, 0, 0, 0, 0,               0,                                                          0,                                0];
+A = jacobian(equationsOfMotion,state_sym);
 % Symbolic description of B matrix
-B = [
-0, 0, 0,                   0;
-0, 0, 0, sin(phi)*sin(Psi) + cos(phi)*cos(Psi)*sin(theta);
-0, 0, 0,                   0;
-0, 0, 0, cos(phi)*sin(Psi)*sin(theta) - cos(Psi)*sin(phi);
[…]

### 2017-08-26 automate.m

@@ -24,5 +24,5 @@ save('runOptions.mat');
 %Run the four scripts
 eoms()
 planOptimalTrajectory()
-% DesignProblemSummer2017('Controller','datafile','data.mat')
-% AnalysisOfOptimalTrajectory()
+DesignProblemSummer2017('Controller','datafile','data.mat')
+AnalysisOfOptimalTrajectory()

### 2017-08-26 eoms.m

@@ -1,5 +1,7 @@
 load('runOptions.mat')
-syms x xdot y ydot z zdot phi theta psi phidot thetadot psidot f1 f2 f3 f4 r real
+syms x xdot y ydot z zdot phi phidot theta thetadot psi psidot f1 f2 f3 f4 r real
+state_sym = [x; xdot; y; ydot; z; zdot; phi; phidot; theta; thetadot; psi; psidot];
+inputs_sym = [f1 f2 f3 f4 r];
 M = [Ix 0 -Ix*sin(theta); ...
     0 Iy*cos(phi)^2+Iz*sin(phi)^2 (Iy-Iz)*cos(phi)*sin(phi)*cos(theta); ...
     -Ix*sin(theta) (Iy-Iz)*cos(phi)*sin(phi)*cos(theta)...
@@ -43,11 +45,11 @@ rho = 1.225;
 Fd = (-.5*c_d*rho*A*norm(vel)^2 *vel)/norm(vel);
 
 equationsOfMotion = [xdot; 
-                    ((f1+f2+f3+f4)/mass)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi))+Fd(1)/mass;
+                    ((f1+f2+f3+f4)/mass)*(cos(psi)*sin(theta)*cos(phi)+sin(psi)*sin(phi))%+Fd(1)/mass;
                     ydot;
-                    ((f1+f2+f3+f4)/mass)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))+Fd(2)/mass;
+                    ((f1+f2+f3+f4)/mass)*(sin(psi)*sin(theta)*cos(phi)-cos(psi)*sin(phi))%+Fd(2)/mass;
                     zdot; 
-                    ((f1+f2+f3+f4)/mass)*cos(theta)*cos(phi)-gravity+Fd(3)/mass;
+                    ((f1+f2+f3+f4)/mass)*cos(theta)*cos(phi)-gravity%+Fd(3)/mass;
                     phidot;
                     nddot(1)
                     thetadot;
@@ -55,4 +57,4 @@ equationsOfMotion = [xdot;
                     psidot;
                     nddot(3)];
 
-save('runOptions.mat','equationsOfMotion','-append');
+save('runOptions.mat','equationsOfMotion','state_sym','inputs_sym','-append');

### 2017-08-28 DesignProblemSummer2017.m
Add files via upload

@@ -97,8 +97,6 @@ process.m = mass;
 process.maxthrust = maxThrust;
 % - Minimum thrust
 process.minthrust = minThrust;
-% - Maximum yaw rate
-process.maxyawrate = maxYawRate;
 
 % DEFINE GEOMETRY
 % Geometry of quadrotor
@@ -144,7 +142,7 @@ controller = eval(process.controller);
 controller.name = process.controller;
 % Parameters
 % - define a list of constants that will be passed to the controller
-names = {'tStep','g','m','maxthrust','minthrust','maxyawrate'};
+names = {'tStep','g','m','maxthrust','minthrust'};
 % - loop to create a structure with only these constants
 controller.parameters = struct;
 for i=1:length(names)
@@ -219,10 +217,10 @@ end
 
 function u = GetInput(process,actuators)
 % Copy input from actuators
- u = [actuators.f1; actuators.f2; actuators.f3; actuators.f4; actuators.r];
+ u = [actuators.f1; actuators.f2; actuators.f3; actuators.f4];
 
 % Initialize inputs to zero
-u = zeros(5,1);
+u = zeros(4,1);
 
 % Copy f1 from actuators
 %==========================================================
@@ -265,15 +263,6 @@ else
     u(4) = actuators.f4;
 end
 
-% Copy r from actuators
-%==========================================================
-if actuators.r< -process.maxyawrate
-    u(5) = -process.maxyawrate;
-elseif actuators.r > process.maxyawrate
-    u(5) = process.maxyawrate;
-else
-    u(5) = actuators.r;
-end
 
 % Add disturbance
 %   (nothing)
@@ -281,6 +270,7 @@ end
 
 function process = Get_Process_From_TandX(t,x,process)
 process.t = t;
+
 process.x = x(1,1);
 process.xdot = x(2,1);
[…]

### 2017-08-28 eoms.m

@@ -1,60 +1,58 @@
 load('runOptions.mat')
-syms x xdot y ydot z zdot phi phidot theta thetadot psi psidot f1 f2 f3 f4 r real
+syms x xdot y ydot z zdot phi phidot theta thetadot psi psidot f1 f2 f3 f4 w1 w2 w3 w4 r real
 state_sym = [x; xdot; y; ydot; z; zdot; phi; phidot; theta; thetadot; psi; psidot];
-inputs_sym = [f1 f2 f3 f4 r];
-M = [Ix 0 -Ix*sin(theta); ...
-    0 Iy*cos(phi)^2+Iz*sin(phi)^2 (Iy-Iz)*cos(phi)*sin(phi)*cos(theta); ...
-    -Ix*sin(theta) (Iy-Iz)*cos(phi)*sin(phi)*cos(theta)...
-    Ix*sin(theta)^2+Iy*sin(phi)^2*cos(theta)^2+Iz*cos(phi)^2*cos(theta)^2];
-c11 = 0;
-c12 = (Iy-Iz)*(thetadot*cos(phi)*sin(phi)+psi*sin(phi)^2*cos(theta)) ...
-    + (Iz-Iy)*psi*cos(phi)^2*cos(theta) - Ix*psi*cos(theta);
-c13 = (Iz-Iy)*psidot*cos(phi)*sin(phi)*cos(theta)^2;
-c21 = (Iz-Iy)*(thetadot*cos(phi)*sin(phi)+psi*sin(phi)^2*cos(theta)) ...
-    + (Iy-Iz)*psi*cos(phi)^2*cos(theta) + Ix*psi*cos(theta);
-c22 = (Iz-Iy)*phidot*cos(phi)*sin(phi);
-c23 = -Ix*psidot*sin(theta)*cos(theta) + Iy*psidot*sin(phi)^2*cos(theta)*sin(theta) ...
-    + Iz*psidot*cos(phi)^2*sin(theta)*cos(theta);
-c31 = (Iy-Iz)*psi*cos(theta)^2*sin(phi)*cos(phi) - Ix*thetadot*cos(theta);
-c32 = (Iz-Iy)*(thetadot*cos(phi)*sin(phi)*sin(theta) + phidot*sin(phi)^2*cos(theta)) ...
-    + (Iy-Iz)*phidot*cos(phi)^2*cos(theta) + Ix*psidot*sin(theta)*cos(theta) ...
[…]

### 2017-08-29 AnalysisOfOptimalTrajectory.m
Add files via upload

@@ -32,13 +32,15 @@ hl = legend('x','y','z','$\dot{x}$','$\dot{y}$','$\dot{z}$','location','northwes
 set(hl, 'Interpreter', 'latex');
 grid on
 xlim([topt(1) topt(end)]);
+xlabel('Time (s)')
 subplot(2,1,2)
 for i = 1:6
     plot(topt,xopt(i,:))
     hold on
 end
 title('OptimTraj Pos & Vel')
-% xlim([topt(1) topt(end)]);
+xlim([topt(1) topt(end)]);
+xlabel('Time (s)')
 hl = legend('x','y','z','$\dot{x}$','$\dot{y}$','$\dot{z}$','location','northwest');
 set(hl, 'Interpreter', 'latex');
 grid on
@@ -52,7 +54,8 @@ end
 title('Simulation Angles')
 hl = legend('$\phi$','$\psi$','$\theta$','$\dot{\phi}$','$\dot{\theta}$','$\dot{\psi}$','location','southwest');
 set(hl, 'Interpreter', 'latex');
-% xlim([topt(1) topt(end)]);
+xlim([topt(1) topt(end)]);
+xlabel('Time (s)')
 ylim([-2 2])
 grid on
 subplot(2,1,2)
@@ -61,8 +64,8 @@ for i = 7:12
     hold on
 end
 title('OptimTraj Angles')
-
-% xlim([topt(1) topt(end)]);
+xlabel('Time (s)')
+xlim([topt(1) topt(end)]);
 hl = legend('$\phi$','$\psi$','$\theta$','$\dot{\phi}$','$\dot{\theta}$','$\dot{\psi}$','location','southwest');
 set(hl, 'Interpreter', 'latex');
 grid on
@@ -75,12 +78,12 @@ for i = 1:4
     hold on
 end
 title('Simulation Input')
-% xlim([topt(1) topt(end)]);
+xlabel('Time (s)')
+xlim([topt(1) topt(end)]);
 % ylim([-10 10])
 grid on
-hl = legend('w1','w2','w3','w4','location','northwest');
-set(hl, 'Interpreter', 'latex');
-% xlabel('$\dot{T}$'),ylabel('$\dot{y}');
+hl = legend('f1','f2','f3','f4','location','northwest');
+
 
 grid on
 subplot(2,1,2)
@@ -89,8 +92,8 @@ for i = 1:4
     hold on
 end
 title('OptimTraj Input')
-
-% xlim([topt(1) topt(end)]);
[…]

### 2017-08-29 Controller.m

@@ -105,21 +105,19 @@ if data.index <= length(data.trajT)
   Time_diff = abs(data.trajT(data.index)-sensors.t);
     
     data.index = data.index + 1;
-    data.index;
     
     trajX = data.trajX(ind);
-    trajXdot = data.trajXdot(ind);
     trajY = data.trajY(ind);
-    trajYdot = data.trajYdot(ind);
     trajZ = data.trajZ(ind);
+    trajXdot = data.trajXdot(ind);
+    trajYdot = data.trajYdot(ind);
     trajZdot = data.trajZdot(ind);
     trajPhi = data.trajPhi(ind);
-    trajPhidot = data.trajPhidot(ind);
     trajTheta = data.trajTheta(ind);
-    trajThetadot = data.trajThetadot(ind);
     trajPsi = data.trajPsi(ind);
+    trajPhidot = data.trajPhidot(ind);
+    trajThetadot = data.trajThetadot(ind);
     trajPsidot = data.trajPsidot(ind);
-    
     trajF1 = data.trajF1(ind);
     trajF2 = data.trajF2(ind);
     trajF3 = data.trajF3(ind);
@@ -128,16 +126,18 @@ if data.index <= length(data.trajT)
 else
     
     trajX = data.trajX(end);
-    trajXdot = data.trajXdot(end);
     trajY = data.trajY(end);
-    trajYdot = data.trajYdot(end);
     trajZ = data.trajZ(end);
+    trajXdot = data.trajXdot(end);
+    
+    trajYdot = data.trajYdot(end);
+    
     trajZdot = data.trajZdot(end);
     trajPhi = data.trajPhi(end);
-    trajPhidot = data.trajPhidot(end);
     trajTheta = data.trajTheta(end);
-    trajThetadot = data.trajThetadot(end);
     trajPsi = data.trajPsi(end);
+    trajPhidot = data.trajPhidot(end);
+    trajThetadot = data.trajThetadot(end);
     trajPsidot = data.trajPsidot(end);
     
     trajF1 = parameters.m*parameters.g/4;
@@ -148,23 +148,27 @@ else
     
 end
 
-A = data.funcA(trajXdot, trajYdot, trajZdot, trajPhi, trajTheta, trajPsi, trajPhidot, trajThetadot, trajPsidot, trajF1, trajF2, trajF3, trajF4);
+A = data.funcA(trajXdot, trajYdot, trajZdot, trajPhi,trajTheta, trajPsi,...
[…]

### 2017-08-29 automate.m

@@ -1,10 +1,10 @@
 % Constants to be applied
 clear; 
-xFinal = 0;
-yFinal = 0;
-zFinal = 5;
-timeDensity = 200;
-runTime = 6;
+xFinal = 2;
+yFinal = 4;
+zFinal = 2;
+timeDensity = 500;
+runTime = 4;
 
 gravity = 9.81;
 mass = 1;

### 2017-08-29 eoms.m

@@ -45,12 +45,9 @@ Tau_b = [tau_phi; tau_theta; tau_psi];
 
 
 equationsOfMotion = [xdot;ydot;zdot;
-    
-        ([0;0;-gravity]+R*Tb/mass);
-        
-        (inv(Rw)*[phidot;thetadot;psidot]);
-        
-        inv(I)*Tau_b-cross(omega_b,I*omega_b)]
+                    ([0;0;-gravity]+R*Tb/mass);
+                    (inv(Rw)*[phidot;thetadot;psidot]);
+                     inv(I)*Tau_b-cross(omega_b,I*omega_b)]
     
 pos = [x;y;z];
 

### 2017-08-29 planOptimalTrajectory.m

@@ -20,8 +20,6 @@ numf = matlabFunction(simplify(equationsOfMotion),'vars',[x y z...
                                                           phi theta psi...
                                                           phidot thetadot psidot...
                                                           f1 f2 f3 f4]);
-numf
-
 problem.func.dynamics = @(t,x,u)( numf(x(1,:), x(2,:), x(3,:),...
                                        x(4,:), x(5,:), x(6,:),...
                                        x(7,:), x(8,:), x(9,:),...

### 2017-08-29 Papers/main.tex
changed input to 4 forces and one moment
Add files via upload

@@
 \usepackage[export]{adjustbox}
+\usepackage{esvect}
+\usepackage{ulem}
 \setlist{nosep,after=\vspace{\baselineskip}}
@@
 \section{Model}
+\subsection{State}
 The motion of the drone is governed by the ordinary differential equations with the state defined as
@@
 \label{state}
-\dot{x} = \begin{bmatrix} \dot{x}\\ \frac{f\sin{\theta}}{m} \\ \dot{z} \\ \frac{f\cos{\theta}}{m} - g \\ \omega \end{bmatrix}
-= \frac{d}{dt}
-\begin{bmatrix} x \\ \dot{x} \\ z \\ \dot{z} \\ \theta 
+x = \begin{bmatrix} x\\y\\z \end{bmatrix},
+\dot{x} = \begin{bmatrix} \dot{x} \\ \dot{y}\\ \dot{z} \end{bmatrix},
+\theta = \begin{bmatrix} \phi\\ \theta\\ \psi \end{bmatrix},
+\dot{\theta} = \begin{bmatrix} \dot{\phi} \\ \dot{\theta}\\ \dot{\psi} \end{bmatrix}
+\end{equation}
+such that $x$ and $z$ correspond to horizontal and vertical position, respectively, while $\phi, \theta, \psi$ correspond to the roll, pitch, and yaw angles respectively.
+However, the angular velocity vector $\omega \neq \dot{\theta}$.
+
+\subsection{Kinematics}
+The angular velocity vector, $\omega$ is not the same as $\dot{\theta}$, which is just the time derivative of the angles\cite{QDSC}.
+To convert the angular velocities into the angular velocity vector, we use the following relation:
+\begin{equation}
+\omega = \begin{bmatrix}
+1 && 0 && 0 \\ 0 && \cos(\phi) && \cos(\theta)\sin(\phi) \\ 0 && -\sin(\phi) && \cos(\theta)\cos(\phi) \end{bmatrix} \dot{\theta}
+\end{equation}
+
+\clearpage
+ The body and inertial frame are related by the rotation matrix R, which goes from the body to inertial frame using the ZYX Euler angle convention.
+
+\begin{equation}
+R = \begin{bmatrix}
+\cos(\psi)\cos(\theta) && \cos(\psi)\sin(\phi)\sin(\theta) - \cos(\phi)\sin(\psi) && \sin(\phi)\sin(\psi) + \cos(\phi)\cos(psi)\sin(\theta) \\
+\cos(\theta)\sin(\psi) && \cos(\phi)\cos(\psi) + \sin(\phi)\sin(\psi)\sin(\theta) && \cos(\phi)\sin(\psi)\sin(\theta) - \cos(\psi)\sin(\phi) \\
+-\sin(\theta) && \cos(\theta)\sin(\phi) && \cos(\phi)\cos(\theta)
 \end{bmatrix} 
 \end{equation}
-such that $x$ and $z$ correspond to horizontal and vertical position, respectively, while $\theta$ corresponds to the angle of the quad from upright. The inputs for the system are defined as
+
+\subsection{Forces}
+The force of each motor is directly proportional to the angular velocity of that motor by:
 \begin{equation}
-\label{inputs}
-u = \begin{bmatrix} \omega \\ f \end{bmatrix}
+T = k\omega^2
 \end{equation}
-such that $\omega$ corresponds to angular pitch rate and $f$ corresponds to thrust.
-Taking the Jacobian lends the following A and B matrices shown by Equation \ref{A_matrix_intermediate} and Equation \ref{B_matrix_intermediate}
+Where  $k$ is a function of different constants unique to the quadrotor and derived in QDSC\cite{QDSC}.
+\newline
+The thrust in the body frame is simply
 \begin{equation}
-\label{A_matrix_intermediate}
-A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && \frac{f\cos{\theta}}{m} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && \frac{-f\sin{\theta}}{m} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
+T_{B} = k \begin{bmatrix}
+0 \\ 0 \\ \omega_{1}^2+\omega_{2}^2+\omega_{3}^2+\omega_{4}^2 \end{bmatrix}
+\end{equation}
+Later on we will discuss future steps and how those constants will allow us to control the power supplied to the motors. But for now, we will simply use the force of each motor in our simulation as: 
+\begin{equation*}
+input(\textit{i}) = f_{i} = \omega_{i}^2
+\end{equation*}
+\newline
+The drag force is calculated by 
+\begin{equation*}
+\vv{F_{D}} = \frac{1}{2} \rho C_{D} A v^2
+\end{equation*}
+For our simulation, we will assume $\vv{F_{D}}$ is $[0,0,0]^T$, because we do not know enough about the quadcopter specs to model it accurately, though we will still include it in the equations of motions.
+
+\subsection{Torques}
+Each rotor contributes some torque about the body axis. The roll (\ref{rolltorque}) and pitch (\ref{pitchtorque}) torque are respectively
+\begin{equation}\label{rolltorque}
+\tau_{\phi} = Lk(f_{3}-f_{1})
+\end{equation}
+\begin{equation} \label{pitchtorque}
+\tau_{\theta} = Lk(f_{4}-f_{2})
+\end{equation}
+and the yaw torque is defined as 
+\begin{equation}
+\tau_{\psi} = b(f_{1}-f_{2}+f_{3}-f_{4})
+\end{equation}
+Where $L$ is the distance from the inertial center of the quadrotor to the $i$th motor.
+$k$ and $b$ are constants defined in \cite{QDSC}.
+The total torque \textit{(without drag)} is $\tau=[\tau_{phi},\tau_{theta},\tau_{psi}]^T$
+
+\subsection{Equations of Motion}
+To start, the velocity and accelerations are simply:
+\begin{equation}
+\dot{x} = \begin{bmatrix} \dot{x}\\ \dot{y} \\ \dot{z} \end{bmatrix}, 
+\ddot{x} =  \begin{bmatrix} 0\\0\\-g \end{bmatrix} + \frac{RT_{B} +F_{D}}{m}
 \end{equation}
 
+The angular velocities in the inertial frame are: 
 \begin{equation}
-\label{B_matrix_intermediate}
-B = \begin{bmatrix} 0 && 0 \\ 0 && \frac{\sin{\theta}}{m} \\ 0 && 0 \\ 0 && \frac{\cos{\theta}}{m} \\ 1 && 0 \end{bmatrix}
+\omega = \begin{bmatrix}
+1 && 0 && 0 \\ 0 && \cos(\phi) && \cos(\theta)\sin(\phi) \\ 0 && -\sin(\phi) && \cos(\theta)\cos(\phi) \end{bmatrix}^{-1} \dot{\theta}
 \end{equation}
+
+Finally, the angular accelerations are defined in equation
+
+\begin{equation}
+\dot{\omega} = I^{-1}(\tau-\omega \times (I\omega))
+\end{equation}
+If $I$, the Inertia Matrix, is axis-symmetric in the form
+\begin{equation*}
+I = \begin{bmatrix} I_{xx} && 0 && 0 \\ 0 && I_{yy} && 0 \\ 0 && 0 && I_{zz} \end{bmatrix},
+\end{equation*}
+then 
+\begin{equation*}
+\dot{\omega} = \begin{bmatrix}
+\tau_{\phi}I_{xx}^{-1} \\ \tau_{\theta}I_{yy}^{-1} \\ \tau_{\psi}I_{zz}^{-1}\end{bmatrix}
+-\begin{bmatrix}
+\frac{I_{yy}-I_{zz}}{I_xx}\omega_{y} \omega_{z} \\ 
+\frac{I_{zz}-I_{xx}}{I_yy}\omega_{x} \omega_{z} \\ 
+\frac{I_{xx}-I_{yy}}{I_zz}\omega_{x} \omega_{y}
+\end{bmatrix}
+\end{equation*}
+
+The matlab code for the forces and torques is simply:
+\begin{quote}
+\begin{lstlisting}
+load('runOptions.mat')
+syms x xdot y ydot z zdot phi phidot theta thetadot psi psidot 
+     	f1 f2 f3 f4 real
+state_sym = [x; xdot; y; ydot; z; zdot; 
+	phi; phidot; theta; thetadot; psi; psidot];
+inputs_sym = [f1 f2 f3 f4];
+
+k = 1;
+b = 1;
+Tb = [0;0;f1+f2+f3+f4];
+
+tau_phi = k*(f3-f1)*dim_1;
+tau_theta = k*(f4-f2)*dim_2;
+tau_psi = b*(f1-f2+f3-f4);
+Tau_b = [tau_phi; tau_theta; tau_psi];
+
+\end{lstlisting}
+\end{quote}
+\clearpage
+The Moment and rotation matrices are then:
+\begin{quote}
+\begin{lstlisting}
+I = [Ix 0 0; 0 Iy 0; 0 0 Iz];
+Rw = [1 0 -sin(theta); 
+           0 cos(phi) cos(theta)*sin(phi); 
+           0 -sin(phi) cos(theta)*cos(phi)];
+
+Rz = [cos(psi) -sin(psi) 0;
+      sin(psi) cos(psi) 0;
+      0 0 1];
+Ry = [cos(theta) 0 sin(theta);
+      0 1 0;
+      -sin(theta) 0 cos(theta)];
+Rx = [1 0 0;
+      0 cos(phi) -sin(phi);
+      0 sin(phi) cos(phi)];
+R= Rz*Ry*Rx;
+
+\end{lstlisting}
+\end{quote}
+Lastly, the equations of motion are easily expressed as:
+\begin{quote}
+\begin{lstlisting}
+equationsOfMotion = [xdot;ydot;zdot;
+                    ([0;0;-gravity]+R*Tb/mass);
+                    (inv(Rw)*[phidot;thetadot;psidot]);
+                     inv(I)*Tau_b-cross(omega_b,I*omega_b)]
+
+\end{lstlisting}
+\end{quote}
+
+\subsection{Linearizion}
+To linearize, we do what we've always done. 
+\begin{quote}
+\begin{lstlisting}
+load('runOptions')
+syms x xdot y ydot z zdot phi phidot theta thetadot psi psidot f1 f2 f3 f4 real
+% Symbolic description of A matrix
+A = jacobian(equationsOfMotion,state_sym);
+% Symbolic description of B matrix
+B = jacobian(equationsOfMotion,inputs_sym);
+
+% Create functions
+data.funcA = matlabFunction(A,'Vars',[xdot ydot zdot phi theta psi phidot thetadot psidot f1 f2 f3 f4]);
+data.funcB = matlabFunction(B,'Vars',[phi theta psi]);
+
+\end{lstlisting}
+\end{quote}
 There is no need to substitute in equilibrium conditions because we will be linearizing about a trajectory.
@@
 syms xdot x zdot z theta w thrust real
-EOMs= [xdot;
-       (thrust/mass)*sin(theta);
-       zdot;
-       (thrust/mass)*cos(theta)-gravity;
-       w];
+EOMs= [xdot;ydot;zdot;
+      ([0;0;-gravity]+R*Tb/mass);
+      (inv(Rw)*[phidot;thetadot;psidot]);
+       inv(I)*Tau_b-cross(omega_b,I*omega_b)];
 
-numf = matlabFunction(EOMs,'vars',[x xdot z zdot theta w thrust]);
-problem.func.dynamics= @(t,x,u) numf( x(1,:),x(2,:),x(3,:),x(4,:),x(5,:),
-                                      u(1,:),u(2,:)) );
+numf = matlabFunction(simplify(equationsOfMotion),...
+   		      'vars',[x y z xdot ydot zdot...
+			      phi theta psi phidot thetadot psidot...
+			      f1 f2 f3 f4]);
+problem.func.dynamics = @(t,x,u)( numf(x(1,:), x(2,:), x(3,:),...
+                                       x(4,:), x(5,:), x(6,:),...
+                                       x(7,:), x(8,:), x(9,:),...
+                                       x(10,:), x(11,:), x(12,:),...
+                                       u(1,:), u(2,:), u(3,:), u(4,:) ));
 
@@
 \subsubsection{Problem Bounds}
-The next step is to set up the \lstinline!problem.bounds!.
+\sout{The next step is to set up the \lstinline!problem.bounds!.
 For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in table \ref{Problem Bounds} below.
-These parameters were chosen so that results of the simulation can be compared to results from D'Andrea's paper\cite{D'Andrea}.
+These parameters were chosen so that results of the simulation can be compared to results from D'Andrea's paper}\cite{D'Andrea}.
+
+The new problem bounds are shown in table \ref{Problem Bounds} below:
 
@@
  $t_{i}$   & 0 s  & Initial time\\
- $t_{f}$  & 2 s  & Final time\\
- $\underline{F}/m$ & 1 m/$s^{2}$ & Min thrust\\
- $\overline{F}/m$ & 20 m/$s^{2}$ & Max thrust\\
- $\overline{\omega}$ & 10 rad/s & Max pitch rate \\
+ $t_{f}$  & 4 s  & Final time\\
+ $\underline{F_{i}}/m$ & $\frac{1}{4}$ m/$s^{2}$ & Min thrust\\
+ $\overline{F_{i}}/m$ & 5 m/$s^{2}$ & Max thrust\\
   \hline
@@
 Using a cost function, an optimized trajectory around any aspect of the simulation can be found. The cost functions available for different variables are shown below. 
+\textcolor{red}{Didn't update the cost functions, lazy}
 \begin{quote}
@@
 % Reference trajectory
+
+% Reference trajectory
 ind = data.index;
-if data.index < length(data.trajT)
+if data.index <= length(data.trajT)    
     trajX = data.trajX(ind);
+    trajY = data.trajY(ind);
+    trajZ = data.trajZ(ind);
+
     trajXdot = data.trajXdot(ind);
-    trajZ = data.trajZ(ind);
+    trajYdot = data.trajYdot(ind);
     trajZdot = data.trajZdot(ind);
+
+    trajPhi = data.trajPhi(ind);
     trajTheta = data.trajTheta(ind);
-    trajW = data.trajW(ind);
-    trajF = data.trajF(ind);
+    trajPsi = data.trajPsi(ind);
+
+    trajPhidot = data.trajPhidot(ind);
+    trajThetadot = data.trajThetadot(ind);
+    trajPsidot = data.trajPsidot(ind);
+
+    trajF1 = data.trajF1(ind);
+    trajF2 = data.trajF2(ind);
+    trajF3 = data.trajF3(ind);
+    trajF4 = data.trajF4(ind);
+
     data.index = data.index + 1;   
-
 \end{lstlisting}
@@
 \begin{lstlisting}
-A = data.funcA(trajTheta,trajF);
-B = data.funcB(trajTheta);
+A = data.funcA(trajXdot, trajYdot, trajZdot, trajPhi,trajTheta, trajPsi,
+               trajPhidot, trajThetadot,trajPsidot, 
+               trajF1, trajF2, trajF3, trajF4);
+B = data.funcB(trajPhi,trajTheta,trajPsi);
 data.K = lqr(A,B,data.Q,data.R);
@@
 
-Finally, the input $u = -Kx + n$ is applied in which $K$ is the previously specified gain matrix, $x$ is the difference between the current state and the trajectory state at the current time, and $n$ is the trajectory input at the current time.
-As an example, when the quadroter is meant to be at hover, $n = -mg$.
-
-\clearpage
+Finally, the input $u = -Kx$ is applied in which $K$ is the previously specified gain matrix and $x$ is the difference between the current state and the trajectory state at the current time.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 xFinal = 5;
+yFinal = 5;
 zFinal = 5;
@@
 
-maxPitchRate = 10;
-maxThrust = 20;
-minThrust = 1;
+maxThrust = 5;
+minThrust = 0.25;
 
@@
 
-In this section, the trajectory for $x=5,z=5$ was analyzed.
-First the Optimal trajectory was calculated and saved, then the simulation was run and data stored, and finally both results were plotted against each other.
-\textbf{Solid lines} show the optimal trajectory, and \textbf{dashed lines} show the simulated quad-rotor path.
-
-Ultimately, the results will be compared to \textbf{one} of D'Andrea's results\cite{D'Andrea}.
+I will \textcolor{red}{\textbf{lazily}} compare different plots of the simulation and optimal trajectory.
 
@@
 tsim = processdata.t;
-xsim = [processdata.x; processdata.xdot; processdata.z; processdata.zdot;    processdata.theta];
-usim = [controllerdata.actuators.pitchrate;...
-	controllerdata.actuators.thrust];
+xsim = [processdata.x; processdata.y; processdata.z;
+        processdata.xdot; processdata.ydot; processdata.zdot; 
+        processdata.phi; processdata.theta;processdata.psi;
+        processdata.phidot; processdata.thetadot; processdata.psidot];
+
+usim = [controllerdata.actuators.f1; 
+        controllerdata.actuators.f2;
+        controllerdata.actuators.f3;
+        controllerdata.actuators.f4];
 \end{lstlisting}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                          Comparison with D'Andrea Results                %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison with D'Andrea Results}
-
-We can compare the simulated trajectory with that of \textit{Performance Benchmarking of Quadrotor Systems Using Time-Optimal Control} \cite{D'Andrea}.
-The trajectory to be compared to from D'Andrea's paper is shown in Figure \ref{D'Andrea Plot}
-
-Reminder, \textbf{Solid lines} show the calculated optimal trajectory. \textbf{Dashed lines} show the simulated quad-rotor path.
-
-\begin{figure}[h!]
-  \centering
-  \begin{minipage}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{State.png}
-    \caption{\label{State Plot} Quadcopter state over time.}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.49\textwidth}
-    \includegraphics[width=\textwidth]{Inputs.png}
-    \caption{\label{Input Plot} Quadcopter Inputs over time.}
-  \end{minipage}
+\begin{figure}[H]
+\centerline{\includegraphics[scale=0.45]{0_0_5.PNG}}
+  \caption{\label{0_0_5} x=0, y=0, z=5}
+  \label{fig}
 \end{figure}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=9cm, height=8.5cm]{DAndrea_55_Plot.png}}
-  \caption{\label{D'Andrea Plot} Screenshot of D'Andrea Results}
+\centerline{\includegraphics[scale=0.45]{5_0_5.PNG}}
+  \caption{\label{5_0_5} x=5, y=0, z=5}
   \label{fig}
@@
 
-Though both results are nearly identical, the biggest difference in performance is in that of the inputs. 
-D'Andrea input for thrust is bang-bang, meaning there is a switch discontinuity and the input only takes the minimum and maximum values \cite{BangBangControl}.
-D'Andrea's pitch rate is bang-singular, meaning the control input is always at full positive or negative saturation, except during singular arcs \cite{D'Andrea}.
-
-In our model, the inputs were free to vary as continuously as possible between the bounds set in table \ref{Problem Bounds}.
-Despite this, both models arrived at the destination $x=z=5$ following approximately the same time-optimal path and input behavior.
-In order to completely match input behavior, this issue may be resolved through tinkering with OptimTraj.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                              D'Andrea Results                                                                        %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
+\centerline{\includegraphics[scale=0.45]{2_4_2.PNG}}
+  \caption{\label{2_4_2} x=2, y=4, z=2}
+  \label{fig}
+\end{figure}
 
@@
 \section{Future Work}
-With the completion of a 2D optimized drone path, plans to enhance the simulation are underway.
-Two main additions will be added to the current simulation in order to complete this task.
-Those are as follows
-\newline
+
 \begin{itemize}
-  \item Implement 3D rigid body dynamics
-  \item Implement additional aerodynamic forces such as drag and ground effect
+  \item \sout{Implement 3D rigid body dynamics}
+  \item \sout{Implement additional aerodynamic forces such as drag and ground effect}
 \end{itemize}
 \textit{Controlling of an Single Drone}\cite{Controlling of an Single Drone} provides an outline for how to linearize a 3D quadcopter using rigid body dynamics.
-A key difference to note is that in the dynamics discussed in \cite{Controlling of an Single Drone}, each of the four quadrotor blades can produce its own thrust, which will then control the pitch, roll, and yaw of the rigid body.
-Additionally, the paper gives a brief description of the mechanism on applying aerodynamic forces, namely, drag.
+A key difference to note is that in the dynamics discussed in {\cite{Controlling of an Single Drone}, each of the four quadrotor blades can produce its own thrust, which will then control the pitch, roll, and yaw of the rigid body.
+Additionally, the paper gives a brief description of the mechanism on applying aerodynamic forces, namely, drag.}
+\newline
+\newline
+\textit{Quadcopter Dynamics, Simulation, and Control}\cite{QDSC} provides the outline as to how we managed to redo the dynamics model.
+It also gives us step by step processes  \textcolor{red}{(outlined a bit by Michael) as to how to control the power and blahh blahh blahh}
 
@@
 
+\bibitem{QDSC}
+\textit{Quadcopter Dynamics, Simulation, and Control}.
+
 \end{thebibliography}

### 2017-08-30 Papers/main.tex

@@
 \clearpage
-The Moment and rotation matrices are then:
+The moment and rotation matrices are then:
 \begin{quote}
@@
 
-The new problem bounds are shown in table \ref{Problem Bounds} below:
+The new problem bounds are derived from the D'Andrea paper but have been adapted to the current model.
+Namely, the thrust values now reflect the per-rotor thrust instead of the total.
+They are shown in table \ref{Problem Bounds} below:
 
@@
 \subsubsection{Cost Function}
-Using a cost function, an optimized trajectory around any aspect of the simulation can be found. The cost functions available for different variables are shown below. 
-\textcolor{red}{Didn't update the cost functions, lazy}
+Using a cost function, an optimized trajectory around any aspect of the simulation can be found. The time optimal cost function is shown below.
 \begin{quote}
 \begin{lstlisting}
-% Input:
-problem.func.pathObj = @(t,x,u)( sum(u.^2,1) );
-
-% Thrust:
-problem.func.pathObj = @(t,x,u)( sum(u(2,:).^2,1) );
-
-% Pitch Rate:
-problem.func.pathObj = @(t,x,u)( sum(u(1,:).^2,1) );
-
-% Time
-problem.func.pathObj = @(t,x,u)( sum((x(1,:)-x_f).^2,1) 
-                                +sum((x(3,:)-z_f).^2,1))
 
@@
 \end{quote}
-For our purposes, we explicitly used the "Time objective function for boundary points" and the other cost functions were commented out.
 
@@
 The preceding lines of code are meant to show how easily the data can be unpacked and plotted against each other.
-Below, Figure \ref{State Plot} shows the optimal and actual state of the quadrotor, and Figure \ref{Input Plot} shows the optimal and actual inputs of the quadrotor.
+The below figures show the trajectory and simulated states and inputs of the quadrotor for varying goal positions.
 \newline
@@
 \textit{Quadcopter Dynamics, Simulation, and Control}\cite{QDSC} provides the outline as to how we managed to redo the dynamics model.
-It also gives us step by step processes  \textcolor{red}{(outlined a bit by Michael) as to how to control the power and blahh blahh blahh}
+It also gives us step-by-step processes on creating a relationship between voltage drop across a motor and the thrust produced by the respective propeller.
+Modelling our control inputs as voltage drops instead of thrusts is a more accurate description of what we will have access to on an actual vehicle, and may serve as preperation for writing flight code.
 
